---
title: "DEFINE-HOUSING-2.0"
date: "2026"
---

TIME PERIODS AND NUMBER OF SCENARIOS

```{r}
rm(list=ls(all=TRUE))
n_periods<-28 
Scenarios<-5
```

EQUATIONS

```{r}
Equations<-function(t){
  #Worker households
  Y_HWG[t]<<-W[t]+int_D*D_HW[t-1]-int_LHC[t-1]*L_HC[t-1]-int_LHG[t-1]*L_HG[t-1]+int_SUB*L_HG[t-1]-Rent[t]
  Y_HW[t]<<-Y_HWG[t]-TAX_HW[t] 
  CO_HW[t]<<-c_11*Y_HW[t-1]+c_12*V_HW[t-1]
  D_HW[t]<<-prop_D*Y_HW[t-1]
  V_HW[t]<<-p_H[t]*H_WOwnG[t]+p_H[t]*H_WOwnC[t]+D_HW[t]-L_HG[t]-L_HC[t]
  NLHG_DN[t]<<-(H_DWOwnG[t]-H_WOwnG[t-1])*p_H[t-1]+rep_L*L_HG[t-1]-beta_H[t]*(Y_HW[t]-CO_HW[t]-(D_HW[t]-D_HW[t-1]))
  NLHC_DN[t]<<-(H_DWOwnC[t]-H_WOwnC[t-1])*p_H[t-1]+rep_L*L_HC[t-1]-(1-beta_H[t])*(Y_HW[t]-CO_HW[t]-(D_HW[t]-D_HW[t-1]))
  L_HG[t]<<-L_HG[t-1]+(1-CR_HG[t])*NLHG_D[t]-rep_L*L_HG[t-1]-def_HW[t]*L_HG[t-1]
  L_HC[t]<<-L_HC[t-1]+(1-CR_HC[t])*NLHC_D[t]-rep_L*L_HC[t-1]-def_HW[t]*L_HC[t-1]
  L_H[t]<<-L_HC[t]+L_HG[t]
  DL_HW[t]<<-def_HW[t]*L_H[t-1]
  def_HW[t]<<-def_max/(1+def_0*exp(def_1-def_2*illiq_HW[t-1]))
  illiq_HW[t]<<-((int_LHG[t-1]+rep_L)*L_HG[t-1]+(int_LHC[t-1]+rep_L)*L_HC[t-1]+TAX_HW[t]+CO_HW[t]+(H_WOwnG[t]-H_WOwnG[t-1])*p_H[t-1]+(H_WOwnC[t]-H_WOwnC[t-1])*p_H[t-1]+Rent[t]-int_SUB*L_HG[t-1])/(W[t]+(1-CR_HG[t])*NLHG_D[t]+(1-CR_HC[t])*NLHC_D[t])
  dsr_HW[t]<<-((int_LHG[t-1]+rep_L)*L_HG[t-1]+(int_LHC[t-1]+rep_L)*L_HC[t-1])/(Y_HW[t]+int_LHG[t-1]*L_HG[t-1]+int_LHC[t-1]*L_HC[t-1])
  lev_HW[t]<<-L_H[t]/(p_H[t]*H_WOwn[t])
  H_DWOwn[t]<<-H_WOwn[t-1]+(h_10-h_11*dsr_HW[t-1]+h_12*g_PH[t-1]+h_13*g_POPW[t-1]+h_14*rent[t])*H_WOwn[t-1]
  beta_H[t]<<-beta_H0-beta_H1*(int_LHG[t-1]-int_SUB-int_LHC[t-1])
  H_DWOwnG[t]<<-beta_H[t]*H_DWOwn[t]
  H_DWOwnC[t]<<-H_DWOwn[t]-H_DWOwnG[t]
  H_WOwn[t]<<-H_WOwn[t-1]+(Y_HW[t]-CO_HW[t]-(D_HW[t]-D_HW[t-1])+L_H[t]-L_H[t-1]+DL_HW[t])/p_H[t]
  H_WOwnG[t]<<-beta_H[t]*H_WOwn[t]
  H_WOwnC[t]<<-H_WOwn[t]-H_WOwnG[t]
  H_WNewOwnOccup[t]<<-prop_W*H_Constr[t]
  H_WNewOwnOccupG[t]<<-beta_H[t]*H_WNewOwnOccup[t]
  H_WNewOwnOccupC[t]<<-H_WNewOwnOccup[t]-H_WNewOwnOccupG[t]
  H_IRentedSold[t]<<-prop_RentedSold*(H_WOwn[t-1]+H_IRent[t-1])
  H_IRentedSoldG[t]<<-beta_H[t]*H_IRentedSold[t]
  H_IRentedSoldC[t]<<-H_IRentedSold[t]-H_IRentedSoldG[t]
  H_WOwnOccup[t]<<-H_WOwn[t]-H_WOwn[t-1]-H_WNewOwnOccup[t]-H_IRentedSold[t]
  H_WOwnOccupG[t]<<-beta_H[t]*H_WOwnOccup[t]
  H_WOwnOccupC[t]<<-H_WOwnOccup[t]-H_WOwnOccupG[t]
  H_IRent[t]<<-H_Workers[t]-H_WOwn[t]
  H_IRentG[t]<<-beta_H[t]*H_IRent[t]
  H_IRentC[t]<<-H_IRent[t]-H_IRentG[t]
  H_INewRented[t]<<-prop_NewRented*H_Constr[t]
  H_INewRentedG[t]<<-beta_H[t]*H_INewRented[t]
  H_INewRentedC[t]<<-H_INewRented[t]-H_INewRentedG[t]
  H_IOwnOccupRented[t]<<-H_IRent[t]-H_IRent[t-1]-H_INewRented[t]+H_IRentedSold[t]+H_IRentedSoldVacant[t]
  H_IOwnOccupRentedG[t]<<-beta_H[t]*H_IOwnOccupRented[t]
  H_IOwnOccupRentedC[t]<<-H_IOwnOccupRented[t]-H_IOwnOccupRentedG[t]
  Rent[t]<<-rent[t]*H_IRent[t-1]
  rent[t]<<-rent[t-1]+(rent_0+rent_1*(g_HDrent[t-1]-g_HSrent[t-1]))*rent[t-1]
  #Investor households
  Y_HIG[t]<<-DP[t]+BP_D[t]+MMFP_D[t]+IFP_D[t]+int_D*D_HI[t-1]+int_S*SEC_HI[t-1]+Rent[t]
  Y_HI[t]<<-Y_HIG[t]-TAX_HI[t] 
  CO_HI[t]<<-c_21*Y_HI[t-1]+c_22*V_HI[t-1]
  V_HI[t]<<-p_H[t]*(H_IOwnG[t]+H_IRentG[t])+p_H[t]*(H_IOwnC[t]+H_IRentC[t])+p_H[t]*(H_Vacant[t]-H_ConstrVacant[t])+D_HI[t]+SEC_HI[t]+SH_MMF[t] 
  SEC_HI[t]<<-(lambda_10+lambda_11*int_S+lambda_12*r_HI[t-1]+lambda_13*r_SH[t-1]+lambda_14*int_D+lambda_15*(Y_HI[t-1]/V_HI[t-1]))*V_HI[t-1]
  H_IOwn[t]<<-((lambda_20+lambda_21*int_S+lambda_22*r_HI[t-1]+lambda_23*r_SH[t-1]+lambda_24*int_D+lambda_25*(Y_HI[t-1]/V_HI[t-1]))*V_HI[t-1])/p_H[t]
  SH_MMF[t]<<-(lambda_30+lambda_31*int_S+lambda_32*r_HI[t-1]+lambda_33*r_SH[t-1]+lambda_34*int_D+lambda_35*(Y_HI[t-1]/V_HI[t-1]))*V_HI[t-1]
  D_HI[t]<<-D_HI[t-1]+Y_HI[t]-CO_HI[t]-(SEC_HI[t]-SEC_HI[t-1])-p_H[t]*H_INewOwnOccup[t]-p_H[t]*H_INewRented[t]+p_H[t]*H_WOwnOccup[t]+p_H[t]*H_IRentedSold[t]-(SH_MMF[t]-SH_MMF[t-1])-I_Refurb[t]
  r_HI[t]<<-rent[t]+(p_H[t]-p_H[t-1])/p_H[t-1]
  r_SH[t]<<-MMFP_D[t]/SH_MMF[t-1]
  H_IOwnG[t]<<-beta_H[t]*H_IOwn[t]
  H_IOwnC[t]<<-H_IOwn[t]-H_IOwnG[t]
  H_WOwnOccupMarket[t]<<-prop_WExisting*H_IOwn[t]
  H_IRentedSoldMarket[t]<<-prop_IRented*H_IOwn[t]
  H_IOwnOccupRentedMarket[t]<<-prop_IOwnOccup*H_IOwn[t]
  H_INewOwnOccup[t]<<-H_IOwn[t]-H_IOwn[t-1]+H_IOwnOccupRented[t]+H_WOwnOccup[t]+H_IRentedVacant[t]+H_WOwnOccupVacant[t]
  H_INewOwnOccupG[t]<<-beta_H[t]*H_INewOwnOccup[t]
  H_INewOwnOccupC[t]<<-H_INewOwnOccup[t]-H_INewOwnOccupG[t]
  #Firms
  Y[t]<<-CO_HW[t]+CO_HI[t]+I[t]+CO_GOV[t]+I_Constr[t]+I_Refurb[t]
  TP_G[t]<<-Y[t]-W[t]-int_C*L_C[t-1]-int_G*L_G[t-1]
  W[t]<<-s_W*Y[t]
  TP[t]<<-TP_G[t]-TAX_F[t]-TAX_C[t]
  RP[t]<<-s_F*TP[t-1]
  DP[t]<<-TP[t]-RP[t]
  r[t]<<-TP[t]/K[t]
  u[t]<<-Y[t]/Y_pot[t]
  Y_pot[t]<<-v*K[t]
  I[t]<<-(alpha_00)/(1+exp(alpha_01-alpha_1*u[t-1]-alpha_2*r[t-1]))*K[t-1] 
  beta[t]<<-beta_0-beta_1*(int_G-int_C)
  I_G[t]<<-beta[t]*I[t]
  I_C[t]<<-I[t]-I_G[t]
  K_G[t]<<-K_G[t-1]+I_G[t]
  K_C[t]<<-K_C[t-1]+I_C[t]
  K[t]<<-K_C[t]+K_G[t]
  L_GN[t]<<-L_G[t-1]+I_G[t]+beta[t]*I_Constr[t]-beta[t]*RP[t]-beta[t]*p_H[t]*(H_WNewOwnOccup[t]+H_INewOwnOccup[t]+H_INewRented[t])
  L_C[t]<<-L_C[t-1]+I_C[t]+I_G[t]+I_ConstrG[t]+I_ConstrC[t]-RP[t]-(L_G[t]-L_G[t-1])-p_H[t]*(H_WNewOwnOccup[t]+H_INewOwnOccup[t]+H_INewRented[t])
  L[t]<<-L_C[t]+L_G[t]
  New_Constr[t]<<-(h_20+h_21*(H_WNewOwnOccup[t-1]+H_INewOwnOccup[t-1]+H_INewRented[t-1])/H_Constr[t-1]+h_22*g_PH[t-1])*H_Constr[t-1]
  H_Constr[t]<<-H_Constr[t-1]+New_Constr[t]
  H_ConstrG[t]<<-beta_H[t]*H_Constr[t]
  H_ConstrC[t]<<-H_Constr[t]-H_ConstrG[t]
  I_Constr[t]<<-p_Constr*H_Constr[t]
  I_ConstrG[t]<<-beta_H[t]*I_Constr[t]
  I_ConstrC[t]<<-I_Constr[t]-I_ConstrG[t]
  New_Refurb[t]<<-H_IRentedSoldG[t-1]+H_WOwnOccupG[t-1]+H_IOwnOccupRentedG[t-1]+H_IRentedVacantG[t-1]+H_IRentedSoldVacantG[t-1]+H_WOwnOccupVacantG[t-1]
  H_Refurb[t]<<-H_Refurb[t-1]+New_Refurb[t]
  I_Refurb[t]<<-p_Refurb*H_Refurb[t]
  p_H[t]<<-p_H[t-1]+(h_33+h_3*(g_HD[t-1]-g_HS[t-1]))*p_H[t-1]
  H_ConstrVacant[t]<<-H_Constr[t]-H_WNewOwnOccup[t]-H_INewOwnOccup[t]-H_INewRented[t]
  H_IRentedSoldVacant[t]<<-H_IRentedSoldMarket[t]-H_IRentedSold[t]
  H_IRentedSoldVacantG[t]<<-beta_H[t]*H_IRentedSoldVacant[t]
  H_IRentedSoldVacantC[t]<<-H_IRentedSoldVacant[t]-H_IRentedSoldVacantG[t]
  H_WOwnOccupVacant[t]<<-H_WOwnOccupMarket[t]-H_WOwnOccup[t]
  H_WOwnOccupVacantG[t]<<-beta_H[t]*H_WOwnOccupVacant[t]
  H_WOwnOccupVacantC[t]<<-H_WOwnOccupVacant[t]-H_WOwnOccupVacantG[t]
  H_IRentedVacant[t]<<-H_INewRented[t]+H_IOwnOccupRentedMarket[t]-H_IOwnOccupRented[t]
  H_IRentedVacantG[t]<<-beta_H[t]*H_IRentedVacant[t]
  H_IRentedVacantC[t]<<-H_IRentedVacant[t]-H_IRentedVacantG[t]
  H_Vacant[t]<<-H_Vacant[t-1]+H_ConstrVacant[t]+H_IRentedSoldVacant[t]+H_IRentedVacant[t]+H_WOwnOccupVacant[t]
  H_VacantG[t]<<-beta_H[t]*H_Vacant[t]
  H_VacantC[t]<<-H_Vacant[t]-H_VacantG[t]
  H_Total[t]<<-H_Total[t-1]+H_Constr[t]
  H_Totalred[t]<<-H_WOwn[t]+H_IOwn[t]+H_IRent[t]+H_Vacant[t]
  H_TotalG[t]<<-H_TotalG[t-1]+H_ConstrG[t]
  H_TotalC[t]<<-H_Total[t]-H_TotalG[t]
  H_Workers[t]<<-POP_W[t]/size
  H_Rentiers[t]<<-POP_R[t]/size
  WealthIndex[t]<<-(V_HI[t]/POP_R[t])/(V_HW[t]/POP_W[t])
  POP[t]<<-(1+g_POP[t])*POP[t-1]
  POP_W[t]<<-prop_Workers*POP[t]
  POP_R[t]<<-POP[t]-POP_W[t]
  #Commercial banks
  BP[t]<<-int_C*L_C[t-1]+int_G*L_G[t-1]+int_LHG[t-1]*L_NHG[t-1]+int_LHC[t-1]*L_HC[t-1]+int_S*SEC_B[t-1]+int_R*Repo[t-1]+FEE[t]+FVCP_D[t]-int_D*D[t-1]-int_A[t-1]*A[t-1]
  D[t]<<-D_HW[t]+D_HI[t]
  CAP[t]<<-CAP[t-1]+BP_U[t]-DL_NH[t]
  BP_U[t]<<-s_B*BP[t-1]
  BP_D[t]<<-BP[t]-BP_U[t]
  DL_NH[t]<<-def_HW[t]*(L_NHG[t-1]+L_HC[t-1])
  s[t]<<-s_0-s_1*(yield_M[t-1]-yield_MT)
  L_SHG[t]<<-s[t]*L_HG[t]
  L_NHG[t]<<-L_HG[t]-L_SHG[t]
  HPM[t]<<-h_1*D[t]
  SEC_B[t]<<- ifelse(iterations > 10 && A_N[t]>0, h_2*D[t], SEC_BN[t])
  A_N[t]<<-A[t-1]+(HPM[t]-HPM[t-1])+(L_G[t]-L_G[t-1])+(L_C[t]-L_C[t-1])+(L_NHG[t]-L_NHG[t-1])+(L_HC[t]-L_HC[t-1])+(SEC_B[t]-SEC_B[t-1])+(Repo[t]-Repo[t-1])-(D[t]-D[t-1])-BP_U[t]+DL_NH[t]
  lev_B[t]<<-(HPM[t]+L_C[t]+L_G[t]+L_NHG[t]+L_HC[t]+SEC_B[t]+Repo[t])/CAP[t]
  CAR[t]<<-CAP[t]/(w_L*(L_C[t]+L_G[t]+L_NHG[t]+L_HC[t])+w_S*SEC_B[t]+w_H*HPM[t]+w_R*Repo[t]) 
  CR_H[t]<<-CR_max/(1+r_0*exp(r_1-r_2*dsr_HW[t-1]+r_3*(CAR[t-1]-CAR_min)))
  CR_HG[t]<<-(1+l_H3*(yield_M[t-1]-yield_MT))*CR_H[t]
  CR_HC[t]<<-(1-l_H3*(yield_M[t-1]-yield_MT))*CR_H[t]
  int_LHG[t]<<-spr_HG[t]+int_A[t]
  int_LHC[t]<<-spr_HC[t]+int_A[t]
  spr_H[t]<<-spr_H0-spr_H1*(CAR[t-1]-CAR_min)+spr_H2*dsr_HW[t-1]
  spr_HG[t]<<-(1+spr_H3*(yield_M[t-1]-yield_MT))*spr_H[t]
  spr_HC[t]<<-(1-spr_H3*(yield_M[t-1]-yield_MT))*spr_H[t]
  #Financial Vehicle Corporations (FVCs)
  FVCP[t]<<-int_LHG[t-1]*L_SHG[t-1]+int_S*SEC_FVC[t-1]-FEE[t]-coupon_M[t-1]*m[t-1]
  FVCP_U[t]<<-s_FVC*FVCP[t-1]
  FVCP_D[t]<<-FVCP[t]-FVCP_U[t]
  coupon_M[t]<<-yield_M[t-1]*p_Mbar
  yield_M[t]<<-coupon_M[t]/p_M[t]
  r_M[t]<<-yield_M[t]+(p_M[t]-p_M[t-1])/p_M[t-1]
  FEE[t]<<-fee*L_SHG[t-1]
  K_FVC[t]<<-K_FVC[t-1]+FVCP_U[t]-DL_FVC[t]
  DL_FVC[t]<<-def_HW[t]*L_SHG[t-1]
  m[t]<<-m[t-1]+(L_SHG[t]-L_SHG[t-1])+DL_FVC[t]
  M[t]<<-M_IF[t]+M_MMF[t]
  p_M[t]<<-M[t]/m[t]
  SEC_FVC[t]<<-SEC_FVC[t-1]+FVCP_U[t]+p_Mbar*(m[t]-m[t-1])-(L_SHG[t]-L_SHG[t-1])-DL_FVC[t]
  #Investment Funds (IF)
  IFP[t]<<-coupon_M[t-1]*m_IF[t-1]+int_S*SEC_IF[t-1]-int_R*Repo[t-1]
  IFP_U[t]<<-s_IF*IFP[t-1]
  IFP_D[t]<<-IFP[t]-IFP_U[t]
  K_IF[t]<<-K_IF[t-1]+IFP_U[t]
  M_IF[t]<<-K_IF[t-1]/haircut[t]-SEC_IF[t]
  haircut[t]<<-epsilon_0+epsilon_1*(yield_M[t-1]-yield_MT)
  m_IF[t]<<-M_IF[t]/p_M[t]
  SEC_IF[t]<<-h_IF*SEC[t]
  Repo[t]<<-Repo[t-1]+p_Mbar*(m_IF[t]-m_IF[t-1])+(SEC_IF[t]-SEC_IF[t-1])-IFP_U[t]
  lev_IF[t]<<-(p_M[t]*m_IF[t]+SEC_IF[t])/K_IF[t]
  #Money Market Funds (MMF)
  MMFP[t]<<-coupon_M[t-1]*m_MMF[t-1]+int_S*SEC_MMF[t-1]
  MMFP_U[t]<<-s_MMF*MMFP[t-1]
  MMFP_D[t]<<-MMFP[t]-MMFP_U[t]
  K_MMF[t]<<-K_MMF[t-1]+MMFP_U[t]
  M_MMF[t]<<-(gamma_10+gamma_11*yield_M[t-1]+gamma_12*int_S)*SH_MMF[t-1]
  SEC_MMF[t]<<-SEC_MMF[t-1]+(SH_MMF[t]-SH_MMF[t-1])-p_Mbar*(m_MMF[t]-m_MMF[t-1])+MMFP_U[t]
  m_MMF[t]<<-M_MMF[t]/p_M[t]
  lev_MMF[t]<<-(p_M[t]*m_MMF[t]+SEC_MMF[t])/SH_MMF[t]
  #Government
  GNS[t]<<-TAX[t]+CBP[t]-CO_GOV[t]-int_SUB*L_HG[t-1]-int_S*SEC[t-1]
  SEC[t]<<-SEC[t-1]-GNS[t]
  CO_GOV[t]<<-gov_C*Y[t-1]
  TAX_HW[t]<<-tau_HW*Y_HWG[t-1]  
  TAX_HI[t]<<-tau_HI*Y_HIG[t-1] 
  TAX_F[t]<<-tau_F*TP_G[t-1] 
  TAX_C[t]<<-tau_C*EMIS_O[t-1]
  TAX[t]<<-TAX_HW[t]+TAX_HI[t]+TAX_F[t]+TAX_C[t]
  #Central bank
  CBP[t]<<-int_A[t-1]*A[t-1]+int_S*SEC_CB[t-1]
  SEC_CB[t]<<-SEC[t]-SEC_HI[t]-SEC_B[t]-SEC_FVC[t]-SEC_IF[t]-SEC_MMF[t]
  SEC_CBred[t]<<-SEC_CB[t-1]+(HPM[t]-HPM[t-1])-(A[t]-A[t-1])
  V_CB[t]<<-A[t]+SEC_CB[t]-HPM[t]
  int_A[t]<<-int_ref+(int_max-int_ref)*L_HC[t]/L_H[t]-(int_ref-int_min)*L_HG[t]/L_H[t]
  #Emissions
  EMIS_H[t]<<-CI_H[t]*H_Total[t]
  CI_H[t]<<-CI_Hmax-((CI_Hmax-CI_Hmin)/(1+exp(-kappa_CIH*(HG_HC[t-1]-1/HG_HC[t-1]-c_CIH))))
  EMIS_O[t]<<-CI_O[t]*Y[t]
  CI_O[t]<<-CI_Omax-((CI_Omax-CI_Omin)/(1+exp(-kappa_CIO*(KG_KC[t-1]-1/KG_KC[t-1]-c_CIO))))
  #Auxiliary equations
  H_TotalGred[t]<<-H_WOwnG[t]+H_IOwnG[t]+H_IRentG[t]+H_VacantG[t]
  H_TotalCred[t]<<-H_Totalred[t]-H_TotalGred[t]
  L_G[t]<<- ifelse(L_GN[t]>0, L_GN[t], 0)
  NLHG_D[t]<<- ifelse(iterations > 10 && NLHG_DN[t]>0, NLHG_DN[t], 0)
  NLHC_D[t]<<- ifelse(iterations > 10 && NLHC_DN[t]>0, NLHC_DN[t], 0)
  D_HIN[t]<<-(lambda_40+lambda_41*int_S+lambda_42*r_HI[t-1]+lambda_43*r_SH[t-1]+lambda_44*int_D+lambda_45*(Y_HI[t-1]/V_HI[t-1]))*V_HI[t-1]
  SEC_BN[t]<<-SEC_B[t-1]-(HPM[t]-HPM[t-1])-(L_G[t]-L_G[t-1])-(L_C[t]-L_C[t-1])-(L_NHG[t]-L_NHG[t-1])-(L_HC[t]-L_HC[t-1])-(Repo[t]-Repo[t-1])+(D[t]-D[t-1])+BP_U[t]-DL_NH[t]
  A[t]<<- ifelse(iterations > 10 && A_N[t]>0, A_N[t], 0)
  g_Y[t]<<-(Y[t]-Y[t-1])/Y[t-1]
  lev[t]<<-L[t]/K[t]
  SEC_Y[t]<<-SEC[t]/Y[t]
  SEC_BY[t]<<-SEC_B[t]/Y[t]
  HPM_Y[t]<<-HPM[t]/Y[t]
  TAX_Y[t]<<-TAX[t]/Y[t] 
  CBP_Y[t]<<-CBP[t]/Y[t]
  CAP_K[t]<<-CAP[t]/K[t]
  V_CBK[t]<<-V_CB[t]/K[t]
  HG_HC[t]<<-H_TotalG[t]/H_TotalC[t]
  KG_KC[t]<<-K_G[t]/K_C[t]
  g_Yper[t]<<-g_Y[t]*100
  SEC_Yper[t]<<-SEC_Y[t]*100
  IncomeIndex[t]<<-(Y_HI[t]/POP_R[t])/(Y_HW[t]/POP_W[t])
  PORT_SECHI[t]<<-SEC_HI[t]/V_HI[t-1] 
  PORT_HDI[t]<<-(p_H[t]*H_IOwn[t])/V_HI[t-1] 
  PORT_SHMMF[t]<<-SH_MMF[t]/V_HI[t-1] 
  PORT_D[t]<<-D_HIN[t]/V_HI[t-1] 
  g_VHW[t]<<-(V_HW[t]-V_HW[t-1])/V_HW[t-1]
  g_YHW[t]<<-(Y_HW[t]-Y_HW[t-1])/Y_HW[t-1]
  g_VHI[t]<<-(V_HI[t]-V_HI[t-1])/V_HI[t-1]
  g_YHI[t]<<-(Y_HI[t]-Y_HI[t-1])/Y_HI[t-1]
  g_K[t]<<-(K[t]-K[t-1])/K[t-1]
  g_KG[t]<<-(K_G[t]-K_G[t-1])/K_G[t-1]
  g_KC[t]<<-(K_C[t]-K_C[t-1])/K_C[t-1]
  g_TP[t]<<-(TP[t]-TP[t-1])/TP[t-1]
  g_TPG[t]<<-(TP_G[t]-TP_G[t-1])/TP_G[t-1]
  g_PH[t]<<-(p_H[t]-p_H[t-1])/p_H[t-1]
  g_PHper[t]<<-g_PH[t]*100
  g_HG[t]<<-(H_ConstrG[t]-H_ConstrG[t-1])/H_ConstrG[t-1]
  g_HC[t]<<-(H_ConstrC[t]-H_ConstrC[t-1])/H_ConstrC[t-1]
  g_HDWOwn[t]<<-(H_DWOwn[t]-H_DWOwn[t-1])/H_DWOwn[t-1]
  g_HDWOwnG[t]<<-(H_DWOwnG[t]-H_DWOwnG[t-1])/H_DWOwnG[t-1]
  g_HDWOwnC[t]<<-(H_DWOwnC[t]-H_DWOwnC[t-1])/H_DWOwnC[t-1]
  g_HWOwn[t]<<-(H_WOwn[t]-H_WOwn[t-1])/H_WOwn[t-1]
  g_HWOwnG[t]<<-(H_WOwnG[t]-H_WOwnG[t-1])/H_WOwnG[t-1]
  g_HWOwnGper[t]<<-g_HWOwnG[t]*100
  g_HWOwnC[t]<<-(H_WOwnC[t]-H_WOwnC[t-1])/H_WOwnC[t-1]
  g_HWNewOwnOccup[t]<<-(H_WNewOwnOccup[t]-H_WNewOwnOccup[t-1])/H_WNewOwnOccup[t-1]
  g_HWNewOwnOccupG[t]<<-(H_WNewOwnOccupG[t]-H_WNewOwnOccupG[t-1])/H_WNewOwnOccupG[t-1]
  g_HWNewOwnOccupC[t]<<-(H_WNewOwnOccupC[t]-H_WNewOwnOccupC[t-1])/H_WNewOwnOccupC[t-1]
  g_HWOwnOccup[t]<<-(H_WOwnOccup[t]-H_WOwnOccup[t-1])/H_WOwnOccup[t-1]
  g_HWOwnOccupG[t]<<-(H_WOwnOccupG[t]-H_WOwnOccupG[t-1])/H_WOwnOccupG[t-1]
  g_HWOwnOccupC[t]<<-(H_WOwnOccupC[t]-H_WOwnOccupC[t-1])/H_WOwnOccupC[t-1]
  g_HIRentedSold[t]<<-(H_IRentedSold[t]-H_IRentedSold[t-1])/H_IRentedSold[t-1]
  g_HIRentedSoldG[t]<<-(H_IRentedSoldG[t]-H_IRentedSoldG[t-1])/H_IRentedSoldG[t-1]
  g_HIRentedSoldC[t]<<-(H_IRentedSoldC[t]-H_IRentedSoldC[t-1])/H_IRentedSoldC[t-1]
  g_HINewRented[t]<<-(H_INewRented[t]-H_INewRented[t-1])/H_INewRented[t-1]
  g_HINewRentedG[t]<<-(H_INewRentedG[t]-H_INewRentedG[t-1])/H_INewRentedG[t-1]
  g_HINewRentedC[t]<<-(H_INewRentedC[t]-H_INewRentedC[t-1])/H_INewRentedC[t-1]
  g_HIOwnOccupRented[t]<<-(H_IOwnOccupRented[t]-H_IOwnOccupRented[t-1])/H_IOwnOccupRented[t-1]
  g_HIOwnOccupRentedG[t]<<-(H_IOwnOccupRentedG[t]-H_IOwnOccupRentedG[t-1])/H_IOwnOccupRentedG[t-1]
  g_HIOwnOccupRentedC[t]<<-(H_IOwnOccupRentedC[t]-H_IOwnOccupRentedC[t-1])/H_IOwnOccupRentedC[t-1]
  g_HIRent[t]<<-(H_IRent[t]-H_IRent[t-1])/H_IRent[t-1]
  g_HIRentG[t]<<-(H_IRentG[t]-H_IRentG[t-1])/H_IRentG[t-1]
  g_HIRentC[t]<<-(H_IRentC[t]-H_IRentC[t-1])/H_IRentC[t-1]
  g_HIOwn[t]<<-(H_IOwn[t]-H_IOwn[t-1])/H_IOwn[t-1]
  g_HINewOwnOccup[t]<<-(H_INewOwnOccup[t]-H_INewOwnOccup[t-1])/H_INewOwnOccup[t-1]
  g_HConstr[t]<<-(H_Constr[t]-H_Constr[t-1])/H_Constr[t-1]
  g_HConstrG[t]<<-(H_ConstrG[t]-H_ConstrG[t-1])/H_ConstrG[t-1]
  g_HConstrGper[t]<<-g_HConstrG[t]*100
  g_HWOwnOccupMarket[t]<<-(H_WOwnOccupMarket[t]-H_WOwnOccupMarket[t-1])/H_WOwnOccupMarket[t-1]
  g_HIRentedSoldMarket[t]<<-(H_IRentedSoldMarket[t]-H_IRentedSoldMarket[t-1])/H_IRentedSoldMarket[t-1]
  g_HIOwnOccupRentedMarket[t]<<-(H_IOwnOccupRentedMarket[t]-H_IOwnOccupRentedMarket[t-1])/H_IOwnOccupRentedMarket[t-1]
  g_HConstrVacant[t]<<-(H_ConstrVacant[t]-H_ConstrVacant[t-1])/H_ConstrVacant[t-1]
  g_HIRentedSoldVacant[t]<<-(H_IRentedSoldVacant[t]-H_IRentedSoldVacant[t-1])/H_IRentedSoldVacant[t-1]
  g_HWOwnOccupVacant[t]<<-(H_WOwnOccupVacant[t]-H_WOwnOccupVacant[t-1])/H_WOwnOccupVacant[t-1]
  g_HIRentedVacant[t]<<-(H_IRentedVacant[t]-H_IRentedVacant[t-1])/H_IRentedVacant[t-1]
  g_HVacant[t]<<-(H_Vacant[t]-H_Vacant[t-1])/H_Vacant[t-1]
  g_HIRentedSoldVacantG[t]<<-(H_IRentedSoldVacantG[t]-H_IRentedSoldVacantG[t-1])/H_IRentedSoldVacantG[t-1]
  g_HWOwnOccupVacantG[t]<<-(H_WOwnOccupVacantG[t]-H_WOwnOccupVacantG[t-1])/H_WOwnOccupVacantG[t-1]
  g_HIRentedVacantG[t]<<-(H_IRentedVacantG[t]-H_IRentedVacantG[t-1])/H_IRentedVacantG[t-1]
  g_HVacantG[t]<<-(H_VacantG[t]-H_VacantG[t-1])/H_VacantG[t-1]
  g_HRefurb[t]<<-(H_Refurb[t]-H_Refurb[t-1])/H_Refurb[t-1]
  g_HTotal[t]<<-(H_Total[t]-H_Total[t-1])/H_Total[t-1]
  g_HTotalred[t]<<-(H_Totalred[t]-H_Totalred[t-1])/H_Totalred[t-1]
  g_HTotalG[t]<<-(H_TotalG[t]-H_TotalG[t-1])/H_TotalG[t-1]
  g_HTotalC[t]<<-(H_TotalC[t]-H_TotalC[t-1])/H_TotalC[t-1]
  g_Rent[t]<<-(Rent[t]-Rent[t-1])/Rent[t-1]
  g_rent[t]<<-(rent[t]-rent[t-1])/rent[t-1]
  g_HD[t]<<-(H_WNewOwnOccup[t]+H_INewRented[t]+H_INewOwnOccup[t]+H_WOwnOccup[t]+H_IRentedSold[t]-(H_WNewOwnOccup[t-1]+H_INewRented[t-1]+H_INewOwnOccup[t-1]+H_WOwnOccup[t-1]+H_IRentedSold[t-1]))/(H_WNewOwnOccup[t-1]+H_INewRented[t-1]+H_INewOwnOccup[t-1]+H_WOwnOccup[t-1]+H_IRentedSold[t-1])
  g_HS[t]<<-(H_Constr[t]+H_WOwnOccupMarket[t]+H_IRentedSoldMarket[t]-(H_Constr[t-1]+H_WOwnOccupMarket[t-1]+H_IRentedSoldMarket[t-1]))/(H_Constr[t-1]+H_WOwnOccupMarket[t-1]+H_IRentedSoldMarket[t-1])
  g_HDrent[t]<<-(H_INewRented[t]+H_IOwnOccupRented[t]-H_INewRented[t-1]-H_IOwnOccupRented[t-1])/(H_INewRented[t-1]+H_IOwnOccupRented[t-1])
  g_HSrent[t]<<-(H_IOwnOccupRentedMarket[t]-H_IOwnOccupRentedMarket[t-1])/H_IOwnOccupRentedMarket[t-1]  
  g_LH[t]<<-(L_H[t]-L_H[t-1])/L_H[t-1]
  g_LHG[t]<<-(L_HG[t]-L_HG[t-1])/L_HG[t-1]
  g_LHC[t]<<-(L_HC[t]-L_HC[t-1])/L_HC[t-1]
  g_L[t]<<-(L[t]-L[t-1])/L[t-1]
  g_LG[t]<<-(L_G[t]-L_G[t-1])/L_G[t-1]
  g_LC[t]<<-(L_C[t]-L_C[t-1])/L_C[t-1]
  g_CAP[t]<<-(CAP[t]-CAP[t-1])/CAP[t-1]
  g_A[t]<<-(A[t]-A[t-1])/A[t-1]
  g_D[t]<<-(D[t]-D[t-1])/D[t-1]
  g_DHW[t]<<-(D_HW[t]-D_HW[t-1])/D_HW[t-1]
  g_DHI[t]<<-(D_HI[t]-D_HI[t-1])/D_HI[t-1]
  g_COHW[t]<<-(CO_HW[t]-CO_HW[t-1])/CO_HW[t-1]
  g_COHI[t]<<-(CO_HI[t]-CO_HI[t-1])/CO_HI[t-1]
  g_I[t]<<-(I[t]-I[t-1])/I[t-1]
  g_IConstr[t]<<-(I_Constr[t]-I_Constr[t-1])/I_Constr[t-1]
  g_IConstrperc[t]<<-g_IConstr[t]*100
  g_LNHG[t]<<-(L_NHG[t]-L_NHG[t-1])/L_NHG[t-1]
  g_SECB[t]<<-(SEC_B[t]-SEC_B[t-1])/SEC_B[t-1]
  g_SEC[t]<<-(SEC[t]-SEC[t-1])/SEC[t-1]
  g_BP[t]<<-(BP[t]-BP[t-1])/BP[t-1]
  g_EMISO[t]<<-(EMIS_O[t]-EMIS_O[t-1])/EMIS_O[t-1]
  g_POP[t]<<-g_Y[t]
  g_POPW[t]<<-(POP_W[t]-POP_W[t-1])/POP_W[t-1]
  g_SECHI[t]<<-(SEC_HI[t]-SEC_HI[t-1])/SEC_HI[t-1]
  g_M[t]<<-(M[t]-M[t-1])/M[t-1]
  g_m[t]<<-(m[t]-m[t-1])/m[t-1]
  g_pM[t]<<-(p_M[t]-p_M[t-1])/p_M[t-1]
  g_SECFVC[t]<<-(SEC_FVC[t]-SEC_FVC[t-1])/SEC_FVC[t-1]
  g_KFVC[t]<<-(K_FVC[t]-K_FVC[t-1])/K_FVC[t-1]
  g_SECIF[t]<<-(SEC_IF[t]-SEC_IF[t-1])/SEC_IF[t-1]
  g_KIF[t]<<-(K_IF[t]-K_IF[t-1])/K_IF[t-1]
  g_SECMMF[t]<<-(SEC_MMF[t]-SEC_MMF[t-1])/SEC_MMF[t-1]
  g_KMMF[t]<<-(K_MMF[t]-K_MMF[t-1])/K_MMF[t-1]
  g_mIF[t]<<-(m_IF[t]-m_IF[t-1])/m_IF[t-1]
  g_MIF[t]<<-(M_IF[t]-M_IF[t-1])/M_IF[t-1]
  g_mMMF[t]<<-(m_MMF[t]-m_MMF[t-1])/m_MMF[t-1]
  g_Repo[t]<<-(Repo[t]-Repo[t-1])/Repo[t-1]
  g_SHMMF[t]<<-(SH_MMF[t]-SH_MMF[t-1])/SH_MMF[t-1]
  g_IFP[t]<<-(IFP[t]-IFP[t-1])/IFP[t-1]
  g_MMFP[t]<<-(MMFP[t]-MMFP[t-1])/MMFP[t-1]
  g_MMMF[t]<<-(M_MMF[t]-M_MMF[t-1])/M_MMF[t-1]
  }
```

PARAMETERS AND INITIAL VALUES

```{r}
Parameters_InitialValues<-function(){
  #####
  #Free 
  #####
  g_Y[1]<<-0.02#Growth rate of output ##Based on Eurostat
  int_C<<-0.05#Interest rate on conventional loans ##Based on ECB
  int_G<<-0.05#Interest rate on green loans  ##Based on ECB
  int_D<<-0.02#Interest rate on deposits ##Based on ECB
  int_ref<<-0.03#Reference interest rate on advances ##Selected from a reasonable range of values
  int_max<<-int_ref#Maximum interest rate on advances ##There is no policy in the first year
  int_min<<-int_ref#Minimum interest rate on advances ##There is no policy in the first year
  int_S<<-0.028#Interest rate on government securities ##Based on ECB
  rep_L<<-0.1#Repayment of loans ##Selected from a reasonable range of values
  c_22<<-0.01#Propensity to consume out of wealth for investor households  ##Selected from a reasonable range of values
  c_12<<-0.01#Propensity to consume out of  wealth for worker households  ##Selected from a reasonable range of values
  s_W<<-0.55#Wage share ##Based on Penn World Table 10.0 (see Feenstra, 2015)
  h_13<<-0.01#Parameter in the worker households' desired demand for houses (growth rate of workers population)  ##Selected from a reasonable range of values
  h_14<<-0.01#Parameter in the worker households' desired demand for houses (rents) ##Selected from a reasonable range of values
  h_3<<-0.02#Parameter in housing prices ##Selected from a reasonable range of values
  rent_1<<-0.01#Parameter linked to the rent equation ##Selected from a reasonable range of values
  CI_Hmax<<-1.2*CI_H[1]#Maximum intensity rate for carbon intensity of houses##Selected from a reasonable range of values
  CI_Hmin<<-0.5*CI_H[1]#Minimum intensity rate for carbon intensity of houses  ##Selected from a reasonable range of values
  CI_H2035<<-0.8*CI_H[1] #Carbon housing intensity target##Selected from a reasonable range of values
  HG_HC2034<<-0.52 #Housing intensity target##Selected from a reasonable range of values
  c_CIH<<-(((H_TotalG[1]/(1+g_HTotalG[1]))/(H_TotalC[1]/(1+g_HTotalC[1])))-1/((H_TotalG[1]/(1+g_HTotalG[1]))/(H_TotalC[1]/(1+g_HTotalC[1]))))+(log((CI_H[1]-CI_Hmin)/(CI_Hmax-CI_H[1])))/((log((CI_H2035-CI_Hmin)/(CI_Hmax-CI_H2035))-log((CI_H[1]-CI_Hmin)/(CI_Hmax-CI_H[1])))/((((H_TotalG[1]/(1+g_HTotalG[1]))/(H_TotalC[1]/(1+g_HTotalC[1])))-1/((H_TotalG[1]/(1+g_HTotalG[1]))/(H_TotalC[1]/(1+g_HTotalC[1]))))-(HG_HC2034-1/HG_HC2034)))#Parameter linking the green to conventional housing stock with carbon housing intensity ##Selected from a reasonable range of values
 kappa_CIH<<- -log((CI_Hmax-CI_Hmin)/(CI_Hmax-CI_H[1])-1)/(((H_TotalG[1]/(1+g_HTotalG[1]))/(H_TotalC[1]/(1+g_HTotalC[1])))-1/((H_TotalG[1]/(1+g_HTotalG[1]))/(H_TotalC[1]/(1+g_HTotalC[1])))-c_CIH)#Parameter linking the green to conventional housing stock with carbon housing intensity ##Selected from a reasonable range of values
  CI_Omax<<-1.2*CI_O[1]#Maximum intensity rate for carbon intensity of other emissions ##Selected from a reasonable range of values
  CI_Omin<<-0.5*CI_O[1]#Minimum intensity rate for carbon intensity of other emissions ##Selected from a reasonable range of values
  CI_O2050<<-0.8*CI_O[1]#Carbon other emission intensity target ##Selected from a reasonable range of values
  KG_KC2034<<-0.59#Capital stock intensity target ##Selected from a reasonable range of values
  c_CIO<<-(((K_G[1]/(1+g_KG[1]))/(K_C[1]/(1+g_KC[1])))-1/((K_G[1]/(1+g_KG[1]))/(K_C[1]/(1+g_KC[1]))))+(log((CI_O[1]-CI_Omin)/(CI_Omax-CI_O[1])))/((log((CI_O2050-CI_Omin)/(CI_Omax-CI_O2050))-log((CI_O[1]-CI_Omin)/(CI_Omax-CI_O[1])))/((((K_G[1]/(1+g_KG[1]))/(K_C[1]/(1+g_KC[1])))-1/((K_G[1]/(1+g_KG[1]))/(K_C[1]/(1+g_KC[1]))))-(KG_KC2034-1/KG_KC2034)))#Parameter linking the green to conventional capital stock with carbon other emissions intensity ##Selected from a reasonable range of values
 kappa_CIO<<- -log((CI_Omax-CI_Omin)/(CI_Omax-CI_O[1])-1)/(((K_G[1]/(1+g_KG[1]))/(K_C[1]/(1+g_KC[1])))-1/((K_G[1]/(1+g_KG[1]))/(K_C[1]/(1+g_KC[1])))-c_CIO)#Parameter linking the green to conventional capital stock with carbon other emissions intensity ##Selected from a reasonable range of values
  beta_1<<-1#Parameter for the green investment share to the interest rate differential ##Selected from a reasonable range of values
  alpha_1_dI_du_max<<-0.0069 #Parameter in the investment function ##Selected from a reasonable range of values
  alpha_2_dI_dr_max<<-0.108 #Parameter in the investment function ##Selected from a reasonable range of values
  alpha_00<<-(I[1]/(K[1]/(1+g_K[1])))*2  #Parameter in investment function ##Selected from a reasonable range of values
  alpha_1<<-(alpha_1_dI_du_max*4)/(alpha_00)  #Parameter in the investment function (related to the sensitivity to the capacity utilisation) ##Selected from a reasonable range of values
  alpha_2<<-(alpha_2_dI_dr_max*4)/(alpha_00)  #Parameter in the investment function (related to the sensitivity to the profit rate) ##Selected from a reasonable range of values
  tau_HW<<-0.15#Worker households tax rate  ##Selected from a reasonable range of values
  def_max<<-0.3 #Maximum default rate of housing loans  ##Selected from a reasonable range of values
  def_2_ddef_dilliq_max<<-0.25 #Parameter in the default rate function  ##Selected from a reasonable range of values
  def_0<<-(def_max/def_HW[1])-1 #Parameter in the default rate function  ##Selected from a reasonable range of values
  def_2<<-(def_2_ddef_dilliq_max)*((1+def_0)^2)/(def_max*def_0)#Parameter in the default rate function  ## Selected from a reasonable range of values
  def_1<<-def_2*illiq_HW[1] #Parameter in the default rate function  ##Selected from a reasonable range of values
  CAR_min<<-0.08#Minimum capital adequacy ratio  ##Based on the Basel III regulatory framework
  CR_max<<-0.5 #Maximum  degree of credit rationing  ##Selected from a reasonable range of values
  CR_initial<<-0.2#Initial degree of credit rationing  ##Selected from a reasonable range of values
  r_2dCRddsrmax<<- 1.02476498 #Parameter in the credit rationing of housing loans  ##Selected from a reasonable range of values
  r_3dCRdCARmax<<- -10#Parameter in the credit rationing of housing loans ##Selected from a reasonable range of values
  r_0<<-(CR_max/CR_initial)-1 #Parameter in the credit rationing of housing loans ##Selected from a reasonable range of values
  r_2<<-(r_2dCRddsrmax *((1+r_0)^2))/(CR_max*r_0) #Parameter in the credit rationing of housing loans ##Selected from a reasonable range of values
  r_3<<- -(r_3dCRdCARmax *((1+r_0)^2))/(CR_max*r_0) #Parameter in the credit rationing of housing loans ##Selected from a reasonable range of values
  w_H<<-0 #Risk weight on high-powered money ##Based on BCBS (2023)
  w_S<<-0 #Risk weight on government securities ##Based on BCBS (2023)
  w_L<<-1#Risk weight on loans ##Based on BCBS (2023)
  w_R<<-0.10#Risk weight on repos ##Based on BCBS (2023)
  spr_H2<<-0.02325 #Parameter in the lending spread on housing loans (debt service ratio) ##Selected from a reasonable range of values
  lambda_12<<- -0.01#Parameter of investor households' portfolio choice ##Selected from a reasonable range of values 
  lambda_13<<- -0.01#Parameter of investor households' portfolio choice ##Selected from a reasonable range of values  
  lambda_14<<- -0.01#Parameter of households' portfolio choice ##Selected from a reasonable range of values  
  lambda_15<<- -0.01#Parameter of households' portfolio choice ##Selected from a reasonable range of values  
  lambda_23<<- -0.01#Parameter of investor households' portfolio choice ##Selected from a reasonable range of values  
  lambda_24<<- -0.01#Parameter of investor households' portfolio choice ##Selected from a reasonable range of values  
  lambda_25<<- -0.01#Parameter of investor households' portfolio choice ##Selected from a reasonable range of values  
  lambda_34<<- -0.01#Parameter of investor households' portfolio choice ##Selected from a reasonable range of values  
  lambda_35<<- -0.01#Parameter of investor households' portfolio choice ##Selected from a reasonable range of values  
  lambda_21<<- lambda_12#Parameter of investor households' portfolio choice##Calculated from the constraint    
  lambda_41<<- lambda_14#Parameter of investor households' portfolio choice##Calculated from the constraint    
  lambda_42<<- lambda_24#Parameter of households' portfolio choice##Calculated from the constraint    
  lambda_43<<- lambda_34#Parameter of investor households' portfolio choice##Calculated from the constraint   
  lambda_31<<- lambda_13#Parameter of investor households' portfolio choice##Calculated from the constraint    
  lambda_32<<- lambda_23#Parameter of investor households' portfolio choice##Calculated from the constraint   
  lambda_11<<- -lambda_21- lambda_31-lambda_41#Parameter of investor households' portfolio choice##Calculated from the constraint   
  lambda_22<<- -lambda_12-lambda_32-lambda_42#Parameter of investor households' portfolio choice##Calculated from the constraint   
  lambda_33<<- -lambda_13-lambda_23-lambda_43#Parameter of investor households' portfolio choice##Calculated from the constraint    
  lambda_44<<- -lambda_14-lambda_24-lambda_34#Parameter of households' portfolio choice##Calculated from the constraint   
  lambda_45<<- -lambda_15-lambda_25-lambda_35#Parameter of households' portfolio choice##Calculated from the constraint  
  int_SUB<<-0.0016#Green loan subsidy rate ##Based on OECD (2024), 0.0003*Y[1]/(L_HG[1]/(1+g_LHG[1]))
  fee<<-0.0057#Fee rate ##Based on Karimov et al (2025)
  yield_MT<<-yield_M[1]#Target yield on green MBSs##Selected from a reasonable range of values 
  s_1<<-1#Parameter in the share of green securitised mortgages ##Selected from a reasonable range of values 
  gamma_11<<-0.01#Parameter of MMFs portfolio choice ##Selected from a reasonable range of values 
  gamma_22<<-0.01#Parameter of MMFs portfolio choice ##Selected from a reasonable range of values 
  gamma_12<<- -0.01#Parameter of MMFs portfolio choice ##Selected from a reasonable range of values 
  gamma_21<<-gamma_12#Parameter of MMFs portfolio choice ##Calculated from the constraint    
  p_Mbar<<-p_M[1]#Par value price of green MBSs (EUR)##Selected from a reasonable range of values
  int_R<<-0.035#Interest rate on repos ##Based on ICMA (2022)
  epsilon_1<<-1#Parameter in haircuts##Selected from a reasonable range of values 
  h_IF<<-0.01#Share of government securities owned by IFs ##Selected from a reasonable range of values
  prop_Vacancy<<-0.11#Vacancy rate, percent of total houses##Based on Based on ECB
  prop_HIRent<<-0.28#Proportion of rented houses, percent of total houses##Based on Based on ECB
  prop_Workers<<-0.6#Share of workers##Selected from a reasonable range of values
  prop_IOwnOccup<<-0.012#Proportion of owned houses rentiers wish to rent##Selected from a reasonable range of values
  prop_IRented<<-0.001#Proportion of rented houses rentiers wish to sell ##Selected from a reasonable range of values
  prop_WExisting<<-0.01#Proportion of owned houses rentiers wish to sell##Selected from a reasonable range of values
  size<<-2.3#Average household size## Based on Eurostat
  Y[1]<<-14.59 #Output (EUR trillion)##Based on Eurostat
  CO_GOV[1]<<-0.21*Y[1]#Government expenditure (EUR trillion)##The proportion of government expenditure in GDP is based on Eurostat
  I[1]<<-0.22*Y[1]-I_Constr[1]-I_Refurb[1]#Investment (EUR trillion)##The proportion of total investment in GDP is based on Eurostat
  I_Refurb[1]<<-0.059*Y[1]-I_Constr[1]#Investment in refurbishment (EUR trillion)##The proportion of investment in dwellings in GDP is based on Eurostat
  I_Constr[1]<<-0.41*0.059*Y[1] #Investment in new houses (EUR trillion) ##The proportion of investment in construction in GDP is based on Eurostat and EOS (2024)
  I_G[1]<<-0.98*0.89 #Green investment (EUR trillion)##Green investment refers to renewable energy investment based on NGFS (2025), 0.89 is the exchange rate 
  POP[1]<<-348#Population (Million people) ##Based on Eurostat
  H_Totalred[1]<<-POP[1]*1.24/size#Total number of houses (Million houses)##Based on ECB
  H_IRent[1]<<-prop_HIRent*H_Totalred[1]#Total number of rented houses (Million houses) ##Based on ECB
  H_IOwn[1]<<-H_Rentiers[1]*1.1 #Number of houses investors own (Million houses)##Selected from a reasonable range of values
  H_IRentedSoldVacant[1]<<-0.0001*prop_Vacancy*H_Totalred[1] #Number of rented houses that are vacant and are not sold (Million houses)##Based on ECB
  H_WOwnOccupVacant[1]<<-0.01*prop_Vacancy*H_Totalred[1] #Number of owned houses that are vacant and are not sold (Million houses)##Based on ECB
  H_IOwnOccupRented[1]<<-0.017*H_IRent[1]#Number of owned houses that are rented (Million houses) ##Selected from a reasonable range of values
  Rent[1]<<-0.116*(CO_HW[1]+CO_HI[1])#Expenditure for rent (EUR trillion)##Based on ECB
  p_H[1]<<-0.22#Price of houses (EUR million)##Based on ECB
  beta_H[1]<<-0.34#Share of green houses to total houses ##Based on BPIE (2022)
  def_HW[1]<<-0.02#Default rate on housing loans ##Based on Eurostat
  int_LHG[1]<<-0.04 #Interest rate on green housing loans ##Based on ECB
  int_LHC[1]<<-0.04 #Interest rate on conv. housing loans ##Based on ECB
  TAX_HI[1]<<-0.1*Y[1]#Taxes on investor households' disposable income (EUR trillion)##Selected from a reasonable range of values   
  TAX_C[1]<<-0.032# Carbon tax revenues (EUR trillion) ##Based on ERCST (2025)
  u[1]<<-0.79 #Capacity utilisation rate ##Based on Eurostat
  lev_B[1]<<-14.7#Leverage ratio of banks ##Based on Eurostat
  SEC[1]<<-0.87*Y[1] #Total outstanding amount of government securities (EUR trillion) ##The government securities in GDP is based on Eurostat
  SEC_B[1]<<-0.66*0.35*Y[1]#Government securities held by banks (EUR trillion)  ##The government securities held by banks in GDP is based on Eurostat and EBA
  HPM[1]<<-0.59*Y[1]#High-powered money (EUR trillion)##The high-powered money in GDP is based on Eurostat
  L[1]<<-0.64*Y[1] #Total loans (EUR trillion)##The loans to the non-financial corporations in GDP is based on Eurostat
  L_H[1]<<-0.56*Y[1] #Household debt, consolidated including Non-profit institutions serving households (NPISH) (EUR trillion)##The loans to the households in percent of GDP is based on Eurostat
  D[1]<<-1.5*Y[1]#Deposits (EUR trillion)##Selected from a reasonable range of values
  D_HW[1]<<-0.1*D[1]#Deposits held by worker households (EUR trillion)##Selected from a reasonable range of values
  D_HIN[1]<<-D_HI[1]#Deposits held by investor households (EUR trillion)##Selected from a reasonable range of values
  EMIS_O[1]<<-(1-0.33)*2.376#Other emissions (GtCO2), 0.33 EEA proportion of building emissions ##Based on NGFS (2025) and EEA (2025)
  EMIS_H[1]<<-0.33*2.376#Housing emissions (GtCO2), 0.33 EEA proportion of building emissions ##Based on NGFS (2025) and EEA (2025)
  L_HG[1]<<-beta_H[1]*L_H[1]#Green housing loans (EUR trillion)##Selected from a reasonable range of values
  L_GN[1]<<-L_G[1] #Green loans (EUR trillion)##Selected from a reasonable range of values
  L_G[1]<<-beta[1]*L[1] #Green loans (EUR trillion)##Selected from a reasonable range of values
  p_M[1]<<-1#Price of green MBSs ##Selected from a reasonable range of values
  yield_M[1]<<-int_S+0.01039#Yield on green MBSs ##Based on Marques-Pinto (2020)
  s[1]<<-0.09#Proportion of green securitised loans ##Based on ECB 
  SEC_FVC[1]<<-0.11*SEC[1]#Government securities held by MMFs (EUR trillion)##Selected from a reasonable range of values
  lev_IF[1]<<-4#Leverage ratio of IFs ##Based on ECB
  M_IF[1]<<-0.4*M[1]#Green MBSs held by IFs (EUR trillion)##Selected from a reasonable range of values
  lev_MMF[1]<<-2.2#Leverage ratio of MMFs ##Based on ECB
  SEC_MMF[1]<<-0.04*SEC[1]#Government securities held by MMFs (EUR trillion)##Selected from a reasonable range of values
  g_VHW[1]<<-g_Y[1] #Growth rate of worker households wealth ##Determined based on the initial growth rate of output
  g_YHW[1]<<-g_Y[1] #Growth rate of worker households income ##Determined based on the initial growth rate of output
  g_VHI[1]<<-g_Y[1] #Growth rate of investor households wealth ##Determined based on the initial growth rate of output
  g_YHI[1]<<-g_Y[1] #Growth rate of investor households income ##Determined based on the initial growth rate of output
  g_K[1]<<-g_Y[1] #Growth rate of capital ##Determined based on the initial growth rate of output
  g_KG[1]<<-g_Y[1] #Growth rate of green capital ##Determined based on the initial growth rate of output
  g_KC[1]<<-g_Y[1] #Growth rate of conv. capital ##Determined based on the initial growth rate of output
  g_TP[1]<<-g_Y[1] #Growth rate of total profit ##Determined based on the initial growth rate of output
  g_TPG[1]<<-g_Y[1] #Growth rate of total gross profit ##Determined based on the initial growth rate of output
  g_PH[1]<<-0 #Growth rate of housing prices ##Selected from a reasonable range of values
  g_PHper[1]<<-0 #Growth rate of housing prices (percent) ##Selected from a reasonable range of values
  g_HG[1]<<-g_Y[1] #Growth rate of green constructed houses ##Determined based on the initial growth rate of output
  g_HC[1]<<-g_Y[1] #Growth rate of conv. constructed houses ##Determined based on the initial growth rate of output
  g_HDWOwnG[1]<<-g_Y[1] #Growth rate of desired green owner-occupied houses ##Determined based on the initial growth rate of output
  g_HDWOwnC[1]<<-g_Y[1] #Growth rate of desired conv. owner-occupied houses ##Determined based on the initial growth rate of output
  g_HDWOwn[1]<<-g_Y[1] #Growth rate of desired owner-occupied houses ##Determined based on the initial growth rate of output
  g_HWOwn[1]<<-g_Y[1] #Growth rate of worker-owned houses ##Determined based on the initial growth rate of output
  g_HWOwnG[1]<<-g_Y[1] #Growth rate of green worker-owned houses ##Determined based on the initial growth rate of output
  g_HWOwnC[1]<<-g_Y[1] #Growth rate of conv. worker-owned houses ##Determined based on the initial growth rate of output
  g_HWNewOwnOccup[1]<<-g_Y[1] #Growth rate of new worker own-occupied houses ##Determined based on the initial growth rate of output
  g_HWNewOwnOccupG[1]<<-g_Y[1] #Growth rate of new green worker own-occupied houses ##Determined based on the initial growth rate of output
  g_HWNewOwnOccupC[1]<<-g_Y[1] #Growth rate of new conv. worker own-occupied houses ##Determined based on the initial growth rate of output
  g_HWOwnOccup[1]<<-g_Y[1] #Growth rate of worker own-occupied houses ##Determined based on the initial growth rate of output
  g_HWOwnOccupG[1]<<-g_Y[1] #Growth rate of green worker own-occupied houses ##Determined based on the initial growth rate of output
  g_HWOwnOccupC[1]<<-g_Y[1] #Growth rate of conv. worker own-occupied houses ##Determined based on the initial growth rate of output
  g_HIRent[1]<<-g_Y[1] #Growth rate of rented houses ##Determined based on the initial growth rate of output
  g_HIRentG[1]<<-g_Y[1] #Growth rate of green rented houses ##Determined based on the initial growth rate of output
  g_HIRentC[1]<<-g_Y[1] #Growth rate of conv. rented houses ##Determined based on the initial growth rate of output
  g_HINewRented[1]<<-g_Y[1] #Growth rate of new rented houses ##Determined based on the initial growth rate of output
  g_HINewRentedG[1]<<-g_Y[1] #Growth rate of new green rented houses ##Determined based on the initial growth rate of output
  g_HINewRentedC[1]<<-g_Y[1] #Growth rate of new conv. rented houses ##Determined based on the initial growth rate of output
  g_HIOwnOccupRented[1]<<-g_Y[1] #Growth rate of own-occupied houses turned rented ##Determined based on the initial growth rate of output
  g_HIOwnOccupRentedG[1]<<-g_Y[1] #Growth rate of green own-occupied houses turned rented ##Determined based on the initial growth rate of output
  g_HIOwnOccupRentedC[1]<<-g_Y[1] #Growth rate of conv. own-occupied houses turned rented ##Determined based on the initial growth rate of output
  g_HIRentedSold[1]<<-g_Y[1] #Growth rate of rented houses sold ##Determined based on the initial growth rate of output
  g_HIRentedSoldG[1]<<-g_Y[1] #Growth rate of green rented houses sold ##Determined based on the initial growth rate of output
  g_HIRentedSoldC[1]<<-g_Y[1] #Growth rate of conv. rented houses sold ##Determined based on the initial growth rate of output
  g_HIOwn[1]<<-g_Y[1] #Growth rate of investor-owned houses ##Determined based on the initial growth rate of output
  g_HINewOwnOccup[1]<<-g_Y[1] #Growth rate of new investor own-occupied houses ##Determined based on the initial growth rate of output
  g_HWOwnOccupMarket[1]<<-g_Y[1] #Growth rate of worker own-occupied market houses ##Determined based on the initial growth rate of output
  g_HIRentedSoldMarket[1]<<-g_Y[1] #Growth rate of rented houses sold on market ##Determined based on the initial growth rate of output
  g_HIOwnOccupRentedMarket[1]<<-g_Y[1] #Growth rate of own-occupied houses rented on market ##Determined based on the initial growth rate of output
  g_HConstr[1]<<-g_Y[1] #Growth rate of constructed houses ##Determined based on the initial growth rate of output
  g_HConstrG[1]<<-g_Y[1] #Growth rate of green constructed houses ##Determined based on the initial growth rate of output
  g_HConstrVacant[1]<<-g_Y[1] #Growth rate of vacant constructed houses ##Determined based on the initial growth rate of output
  g_HIRentedSoldVacant[1]<<-g_Y[1] #Growth rate of vacant rented houses sold ##Determined based on the initial growth rate of output
  g_HWOwnOccupVacant[1]<<-g_Y[1] #Growth rate of vacant worker own-occupied houses ##Determined based on the initial growth rate of output
  g_HIRentedVacant[1]<<-g_Y[1] #Growth rate of vacant rented houses ##Determined based on the initial growth rate of output
  g_HVacant[1]<<-g_Y[1] #Growth rate of vacant houses ##Determined based on the initial growth rate of output
  g_HIRentedSoldVacantG[1]<<-g_Y[1] #Growth rate of vacant green rented houses sold ##Determined based on the initial growth rate of output
  g_HWOwnOccupVacantG[1]<<-g_Y[1] #Growth rate of vacant green worker own-occupied houses ##Determined based on the initial growth rate of output
  g_HIRentedVacantG[1]<<-g_Y[1] #Growth rate of vacant green rented houses ##Determined based on the initial growth rate of output
  g_HVacantG[1]<<-g_Y[1] #Growth rate of vacant green houses ##Determined based on the initial growth rate of output
  g_HRefurb[1]<<-g_Y[1] #Growth rate of refurbished houses ##Determined based on the initial growth rate of output
  g_HTotal[1]<<-g_Y[1] #Growth rate of total houses ##Determined based on the initial growth rate of output
  g_HTotalred[1]<<-g_Y[1] #Growth rate of total houses (redundant check) ##Determined based on the initial growth rate of output
  g_HTotalG[1]<<-g_Y[1] #Growth rate of total green houses ##Determined based on the initial growth rate of output
  g_HTotalC[1]<<-g_Y[1] #Growth rate of total conv. houses ##Determined based on the initial growth rate of output
  g_Rent[1]<<-g_Y[1] #Growth rate of rent expenditure ##Determined based on the initial growth rate of output
  g_rent[1]<<-0 #Growth rate of rent rate ##Selected from a reasonable range of values
  g_HD[1]<<-g_Y[1] #Growth rate of housing demand ##Determined based on the initial growth rate of output
  g_HS[1]<<-g_Y[1] #Growth rate of housing supply ##Determined based on the initial growth rate of output
  g_HDrent[1]<<-g_Y[1] #Growth rate of demanded rented houses ##Determined based on the initial growth rate of output
  g_HSrent[1]<<-g_Y[1] #Growth rate of supplied rented houses ##Determined based on the initial growth rate of output
  g_LH[1]<<-g_Y[1] #Growth rate of household loans ##Determined based on the initial growth rate of output
  g_LHG[1]<<-g_Y[1] #Growth rate of green housing loans ##Determined based on the initial growth rate of output
  g_LHC[1]<<-g_Y[1] #Growth rate of conv. housing loans ##Determined based on the initial growth rate of output
  g_D[1]<<-g_Y[1] #Growth rate of deposits ##Determined based on the initial growth rate of output
  g_DHW[1]<<-g_Y[1] #Growth rate of worker household deposits ##Determined based on the initial growth rate of output
  g_DHI[1]<<-g_Y[1] #Growth rate of investor household deposits ##Determined based on the initial growth rate of output
  g_COHW[1]<<-g_Y[1] #Growth rate of worker household consumption ##Determined based on the initial growth rate of output
  g_COHI[1]<<-g_Y[1] #Growth rate of investor household consumption ##Determined based on the initial growth rate of output
  g_I[1]<<-g_Y[1] #Growth rate of investment ##Determined based on the initial growth rate of output
  g_IConstr[1]<<-g_Y[1] #Growth rate of construction investment ##Determined based on the initial growth rate of output
  g_IConstrperc[1]<<-g_IConstr[1]*100 #Growth rate of construction investment (percent) ##Determined based on the initial growth rate of output
  g_L[1]<<-g_Y[1] #Growth rate of total loans ##Determined based on the initial growth rate of output
  g_LG[1]<<-g_Y[1] #Growth rate of green loans ##Determined based on the initial growth rate of output
  g_LC[1]<<-g_Y[1] #Growth rate of conv. loans ##Determined based on the initial growth rate of output
  g_CAP[1]<<-g_Y[1] #Growth rate of bank capital ##Determined based on the initial growth rate of output
  g_A[1]<<-g_Y[1] #Growth rate of advances ##Determined based on the initial growth rate of output
  g_LNHG[1]<<-g_Y[1] #Growth rate of non-securitised green housing loans ##Determined based on the initial growth rate of output
  g_SECB[1]<<-g_Y[1] #Growth rate of government securities held by banks ##Determined based on the initial growth rate of output
  g_SEC[1]<<-g_Y[1] #Growth rate of government securities ##Determined based on the initial growth rate of output
  g_BP[1]<<-g_Y[1] #Growth rate of bank profits ##Determined based on the initial growth rate of output
  g_EMISO[1]<<-g_Y[1] #Growth rate of other emissions ##Determined based on the initial growth rate of output
  g_POP[1]<<-g_Y[1] #Growth rate of population ##Determined based on the initial growth rate of output
  g_POPW[1]<<-g_Y[1] #Growth rate of worker population ##Determined based on the initial growth rate of output
  g_SECHI[1]<<-g_Y[1] #Growth rate of government securities held by investor households ##Determined based on the initial growth rate of output
  g_M[1]<<-g_Y[1] #Growth rate of value of green MBSs ##Determined based on the initial growth rate of output
  g_pM[1]<<-0 #Growth rate of green MBS price ##Selected from a reasonable range of values
  g_SECFVC[1]<<-g_Y[1] #Growth rate of government securities held by FVCs ##Determined based on the initial growth rate of output
  g_KFVC[1]<<-g_Y[1] #Growth rate of FVC capital ##Determined based on the initial growth rate of output
  g_SECIF[1]<<-g_Y[1] #Growth rate of government securities held by IFs ##Determined based on the initial growth rate of output
  g_KIF[1]<<-g_Y[1] #Growth rate of IF capital ##Determined based on the initial growth rate of output
  g_SECMMF[1]<<-g_Y[1] #Growth rate of government securities held by MMFs ##Determined based on the initial growth rate of output
  g_KMMF[1]<<-g_Y[1] #Growth rate of MMF capital ##Determined based on the initial growth rate of output
  g_mIF[1]<<-g_Y[1] #Growth rate of number of green MBSs held by IFs ##Determined based on the initial growth rate of output
  g_MIF[1]<<-g_Y[1] #Growth rate of value of green MBSs held by IFs ##Determined based on the initial growth rate of output
  g_mMMF[1]<<-g_Y[1] #Growth rate of number of green MBSs held by MMFs ##Determined based on the initial growth rate of output
  g_Repo[1]<<-g_Y[1] #Growth rate of repos ##Determined based on the initial growth rate of output
  g_SHMMF[1]<<-g_Y[1] #Growth rate of MMF shares ##Determined based on the initial growth rate of output
  g_IFP[1]<<-g_Y[1] #Growth rate of IF profits ##Determined based on the initial growth rate of output
  g_MMFP[1]<<-g_Y[1] #Growth rate of MMF profits ##Determined based on the initial growth rate of output
  g_MMMF[1]<<-g_Y[1] #Growth rate of value of green MBSs held by MMFs ##Determined based on the initial growth rate of output
  ###################
  #Model-constrained 
  ###################
  #Worker households
  Y_HWG[1]<<-W[1]+int_D*D_HW[1]/(1+g_DHW[1])-int_LHC[1]*L_HC[1]/(1+g_LHC[1])-int_LHG[1]*L_HG[1]/(1+g_LHG[1])+int_SUB*L_HG[1]/(1+g_LHG[1])-Rent[1]#Gross disposable income of the worker households (EUR trillion)##Calculated from Eq. (Y_HWG)
  Y_HW[1]<<-Y_HWG[1]-TAX_HW[1]#Disposable income of the worker households (EUR trillion)##Calculated from Eq. (Y_HW)
  prop_D<<-D_HW[1]/(Y_HW[1]/(1+g_YHW[1]))#Proportion of workers' deposits to income ##Calculated from Eq. (D_HW)
  c_11<<-(CO_HW[1]-c_12*V_HW[1]/(1+g_VHW[1]))/(Y_HW[1]/(1+g_YHW[1]))#Propensity to consume out of disposable income for worker households ##Calculated from Eq. (CO_HW)
  V_HW[1]<<-p_H[1]*H_WOwnG[1]+p_H[1]*H_WOwnC[1]+D_HW[1]-L_HG[1]-L_HC[1]#Wealth of worker households (EUR trillion) ##Calculated from Eq. (V_HW)
  NLHG_DN[1]<<-(H_DWOwnG[1]-H_WOwnG[1]/(1+g_HWOwnG[1]))*p_H[1]/(1+g_PH[1])+rep_L*L_HG[1]/(1+g_LHG[1])-beta_H[1]*(Y_HW[1]-CO_HW[1]-(D_HW[1]-D_HW[1]/(1+g_DHW[1])))#Desired new amount of green housing loans (EUR trillion) ##Calculated from Eq. (NLHG_DN)
  NLHG_D[1]<<-NLHG_DN[1]# ##Calculated from Eq. (NLHG_D)
  NLHC_DN[1]<<-(H_DWOwnC[1]-H_WOwnC[1]/(1+g_HWOwnC[1]))*p_H[1]/(1+g_PH[1])+rep_L*L_HC[1]/(1+g_LHC[1])-(1-beta_H[1])*(Y_HW[1]-CO_HW[1]-(D_HW[1]-D_HW[1]/(1+g_DHW[1])))#Desired new amount of conv. housing loans (EUR trillion)##Calculated from Eq. (NLHC_DN)
  NLHC_D[1]<<-NLHC_DN[1]# ##Calculated from Eq. (NLHC_D)
  H_DWOwn[1]<<-((L_H[1]-L_H[1]/(1+g_LH[1])+rep_L*L_H[1]/(1+g_LH[1])+def_HW[1]*L_H[1]/(1+g_LH[1]))/(1-CR_HC[1])-rep_L*L_H[1]/(1+g_LH[1])+(Y_HW[1]-CO_HW[1]-(D_HW[1]-D_HW[1]/(1+g_DHW[1]))))/p_H[1]+H_WOwn[1]/(1+g_HWOwn[1])#Number of houses workers desire to buy (Million houses) ##Calculated from Eq. (L_H),(L_HG),(L_HC), (NLHG_D) and (NLHC_D) 
  L_HC[1]<<-L_H[1]-L_HG[1]#Conv. housing loans (EUR trillion)##Calculated from Eq. (L_H)
  DL_HW[1]<<-def_HW[1]*L_H[1]/(1+g_LH[1])#Amount of defaulted loans (EUR trillion) ##Calculated from Eq. (DL_HW)
  illiq_HW[1]<<-((int_LHG[1]+rep_L)*L_HG[1]/(1+g_LHG[1])+(int_LHC[1]+rep_L)*L_HC[1]/(1+g_LHC[1])+TAX_HW[1]+CO_HW[1]+(H_WOwnG[1]-H_WOwnG[1]/(1+g_HWOwnG[1]))*p_H[1]/(1+g_PH[1])+(H_WOwnC[1]-H_WOwnC[1]/(1+g_HWOwnC[1]))*p_H[1]/(1+g_PH[1])+Rent[1]-int_SUB*L_HG[1]/(1+g_LHG[1]))/(W[1]+(1-CR_HG[1])*NLHG_D[1]+(1-CR_HC[1])*NLHC_D[1])#Worker households' illiquidity ratio ##Calculated from Eq. (illiq_HW)
  dsr_HW[1]<<-((int_LHG[1]+rep_L)*L_HG[1]/(1+g_LHG[1])+(int_LHC[1]+rep_L)*L_HC[1]/(1+g_LHC[1]))/(Y_HW[1]+int_LHG[1]*L_HG[1]/(1+g_LHG[1])+int_LHC[1]*L_HC[1]/(1+g_LHC[1]))#Debt service ratio of worker households ##Calculated from Eq. (dsr_HW)
  lev_HW[1]<<-L_H[1]/(p_H[1]*H_WOwn[1])#Leverage ratio of worker households ##Calculated from Eq. (lev_HW)
  h_10<<-(H_DWOwn[1]-H_WOwn[1]/(1+g_HWOwn[1]))/(H_WOwn[1]/(1+g_HWOwn[1]))+h_11*dsr_HW[1]-h_12*g_PH[1]-h_13*g_POPW[1]-h_14*rent[1]#Parameter in the worker households' desired demand for houses ##Calculated from Eq. (H_DWOwn)
  H_DWOwnG[1]<<-beta_H[1]*H_DWOwn[1]#Number of green houses workers desire to buy (Million houses) ##Calculated from Eq. (H_DWOwnG)
  beta_H0<<-beta_H[1]+beta_H1*(int_LHG[1]-int_SUB-int_LHC[1])#Parameter in share of green houses ##Calculated from Eq. (beta_H)
  H_DWOwnC[1]<<-H_DWOwn[1]-H_DWOwnG[1]#Number of conv. houses workers desire to buy (Million houses) ##Calculated from Eq. (H_DWOwnC)
  CO_HW[1]<<- -(H_WOwn[1]-H_WOwn[1]/(1+g_HWOwn[1]))*p_H[1]+Y_HW[1]-(D_HW[1]-D_HW[1]/(1+g_DHW[1]))+L_H[1]-L_H[1]/(1+g_LH[1])+DL_HW[1]#Consumption of worker households (EUR trillion)##Calculated from Eq. (H_WOwn)
  H_WOwnG[1]<<-beta_H[1]*H_WOwn[1]#Number of green houses workers buy (Million houses) ##Calculated from Eq. (H_WOwnG)
  H_WOwnC[1]<<-H_WOwn[1]-H_WOwnG[1]#Number of conv. houses workers buy (Million houses) ##Calculated from Eq. (H_WOwnC)
  prop_W<<-H_WNewOwnOccup[1]/H_Constr[1]#Proportion of new own-occupied houses by workers to total new houses ##Calculated from Eq. (H_WNewOwnOccup)
  H_WNewOwnOccupG[1]<<-beta_H[1]*H_WNewOwnOccup[1]#Number of new green houses workers buy (Million houses) ##Calculated from Eq. (H_WNewOwnOccupG)
  H_WNewOwnOccupC[1]<<-H_WNewOwnOccup[1]-H_WNewOwnOccupG[1]#Number of new conv. houses workers buy (Million houses) ##Calculated from Eq. (H_WNewOwnOccupC)
  prop_RentedSold<<-H_IRentedSold[1]/((H_WOwn[1]/(1+g_HWOwn[1])+H_IRent[1]/(1+g_HIRent[1])))#Proportion of rented houses that were sold ##Calculated from Eq. (H_IRentedSold)
  H_IRentedSoldG[1]<<-beta_H[1]*H_IRentedSold[1]#Number of green rented houses that were sold (Million houses) ##Calculated from Eq. (H_IRentedSoldG)
  H_IRentedSoldC[1]<<-H_IRentedSold[1]-H_IRentedSoldG[1]#Number of conv. rented houses that were sold (Million houses) ##Calculated from Eq. (H_IRentedSoldC)
  H_WNewOwnOccup[1]<<-H_WOwn[1]-H_WOwn[1]/(1+g_HWOwn[1])-H_IRentedSold[1]-H_WOwnOccup[1]#Number of new own-occupied houses of workers (Million houses) ##Calculated from Eq. (H_WOwnOccup)
  H_WOwnOccupG[1]<<-beta_H[1]*H_WOwnOccup[1]#Number of new green own-occupied houses of workers (Million houses) ##Calculated from Eq. (H_WOwnOccupG)
  H_WOwnOccupC[1]<<-H_WOwnOccup[1]-H_WOwnOccupG[1]#Number of new conv. own-occupied houses of workers (Million houses) ##Calculated from Eq. (H_WOwnOccupC)
  H_INewRented[1]<<-(g_HIRent[1]/(1+g_HIRent[1]))*H_IRent[1]-H_IOwnOccupRented[1]+H_IRentedSoldMarket[1]#Number of new rented houses (Million houses) ##Calculated from Eq. (H_IOwnOccupRented) and Eq. (H_IRentedSoldVacant)
  H_IRentedSoldVacantG[1]<<-beta_H[1]*H_IRentedSoldVacant[1]#Number of green rented houses that are vacant (Million houses) ##Calculated from Eq. (H_IRentedSoldVacantG)
  H_IRentedSoldVacantC[1]<<-H_IRentedSoldVacant[1]-H_IRentedSoldVacantG[1]#Number of conv. rented houses that are vacant (Million houses) ##Calculated from Eq. (H_IRentedSoldVacantC)
  H_IRentedVacant[1]<<-H_INewRented[1]+H_IOwnOccupRentedMarket[1]-H_IOwnOccupRented[1]#Number of rented houses that are vacant (Million houses) ##Calculated from Eq. (H_IRentedVacant)
  H_IRentedVacantG[1]<<-beta_H[1]*H_IRentedVacant[1]#Number of green rented houses that are vacant (Million houses) ##Calculated from Eq. (H_IRentedVacantG)
  H_IRentedVacantC[1]<<-H_IRentedVacant[1]-H_IRentedVacantG[1]#Number of conv. rented houses that are vacant (Million houses) ##Calculated from Eq. (H_IRentedVacantC)
  H_IRentedSold[1]<<-H_IRentedSoldMarket[1]-H_IRentedSoldVacant[1]#Number of rented houses that are sold (Million houses) ##Calculated from Eq. (H_IRentedSoldVacant)
  H_WOwn[1]<<-H_Workers[1]-H_IRent[1] #Number of houses workers own (Million houses)##Calculated from Eq. (H_IRent)
  H_IRentG[1]<<-beta_H[1]*H_IRent[1]#Number of green rented houses (Million houses) ##Calculated from Eq. (H_IRentG)
  H_IRentC[1]<<-H_IRent[1]-H_IRentG[1]#Number of conv. rented houses (Million houses) ##Calculated from Eq. (H_IRentC)
  H_INewRentedG[1]<<-beta_H[1]*H_INewRented[1]#Number of green new rented houses (Million houses) ##Calculated from Eq. (H_INewRentedG)
  H_INewRentedC[1]<<-H_INewRented[1]-H_INewRentedG[1]#Number of new conv. rented houses (Million houses) ##Calculated from Eq. (H_INewRentedC)
  prop_NewRented<<-H_INewRented[1]/H_Constr[1]#Proportion of new rented houses ##Calculated from Eq. (H_INewRented)
  H_IOwnOccupRentedG[1]<<-beta_H[1]*H_IOwnOccupRented[1]#Number of green rented houses that were own-occupied by rentiers (Million houses) ##Calculated from Eq. (H_IOwnOccupRentedG)
  H_IOwnOccupRentedC[1]<<-H_IOwnOccupRented[1]-H_IOwnOccupRentedG[1]#Number of conv. rented houses that were own-occupied by rentiers (Million houses)##Calculated from Eq. (H_IOwnOccupRentedC)
  rent[1]<<-Rent[1]/(H_IRent[1]/(1+g_HIRent[1]))#Rent rate (EUR million) ##Calculated from Eq. (Rent)
  rent_0<<-g_rent[1]-rent_1*(g_HDrent[1]-g_HSrent[1])#Parameter linked to the rent equation ##Calculated from Eq. (rent)
  #Investor households
  Y_HIG[1]<<-DP[1]+BP_D[1]+MMFP_D[1]+IFP_D[1]+int_D*D_HI[1]/(1+g_DHI[1])+int_S*SEC_HI[1]/(1+g_SECHI[1])+Rent[1]#Gross disposable income of the investor households (EUR trillion)##Calculated from Eq. (Y_HIG)
  Y_HI[1]<<-Y_HIG[1]-TAX_HI[1] #Disposable income of the investor households (EUR trillion) ##Calculated from Eq. (Y_HI)
  c_21<<-(CO_HI[1]-c_22*V_HI[1]/(1+g_VHI[1]))/(Y_HI[1]/(1+g_YHI[1]))#Propensity to consume out of disposable income for investor households  ##Calculated from Eq. (CO_HI)
  V_HI[1]<<-p_H[1]*(H_IOwnG[1]+H_IRentG[1])+p_H[1]*(H_IOwnC[1]+H_IRentC[1])+p_H[1]*(H_Vacant[1]-H_ConstrVacant[1])+D_HI[1]+SEC_HI[1]+SH_MMF[1]#Wealth of investor households (EUR trillion) ##Calculated from Eq. (V_HI)
  lambda_10<<-SEC_HI[1]/(V_HI[1]/(1+g_VHI[1]))-(lambda_11*int_S+lambda_12*r_HI[1]+lambda_13*r_SH[1]+lambda_14*int_D+lambda_15*(Y_HI[1]/V_HI[1]))#Parameter of investor households' portfolio choice ##Calculated from Eq. (SEC_HI)
  lambda_20<<-(p_H[1]*H_IOwn[1])/(V_HI[1]/(1+g_VHI[1]))-(lambda_21*int_S+lambda_22*r_HI[1]+lambda_23*r_SH[1]+lambda_24*int_D+lambda_25*(Y_HI[1]/V_HI[1]))#Parameter of investor households' portfolio choice ##Calculated from Eq. (H_IOwn)
  lambda_30<<-SH_MMF[1]/(V_HI[1]/(1+g_VHI[1]))-(lambda_31*int_S+lambda_32*r_HI[1]+lambda_33*r_SH[1]+lambda_34*int_D+lambda_35*(Y_HI[1]/V_HI[1]))#Parameter of investor households' portfolio choice ##Calculated from Eq. (SH_MMF)
  lambda_40<<-D_HIN[1]/(V_HI[1]/(1+g_VHI[1]))-(lambda_41*int_S+lambda_42*r_HI[1]+lambda_43*r_SH[1]+lambda_44*int_D+lambda_45*(Y_HI[1]/V_HI[1]))#Parameter of investor households' portfolio choice ##Calculated from Eq. (D_HIN)
  r_HI[1]<<-rent[1]+(p_H[1]-p_H[1]/(1+g_PH[1]))/(p_H[1]/(1+g_PH[1]))#Rate of return for houses ##Calculated from Eq. (r_HI)
  r_SH[1]<<-MMFP_D[1]/(SH_MMF[1]/(1+g_SHMMF[1]))#Rate of return on shares issued by MMFs ##Calculated from Eq. (r_SH)
  H_IOwnG[1]<<-beta_H[1]*H_IOwn[1]#Number of green own-occupied houses by rentiers (Million houses) ##Calculated from Eq. (H_IOwnG)
  H_IOwnC[1]<<-H_IOwn[1]-H_IOwnG[1]#Number of conv. own-occupied houses by rentiers (Million houses) ##Calculated from Eq. (H_IOwnC)
  H_WOwnOccupMarket[1]<<-prop_WExisting*H_IOwn[1]#Number of own-occupied houses by rentiers for selling (Million houses) ##Calculated from Eq. (H_WOwnOccupMarket)
  H_IOwnOccupRentedMarket[1]<<-prop_IOwnOccup*H_IOwn[1]#Number of own-occupied houses by rentiers for renting (Million houses) ##Calculated from Eq. (H_IOwnOccupRentedMarket)
  H_IRentedSoldMarket[1]<<-prop_IRented*H_IOwn[1]#Number of rented houses by rentiers for selling (Million houses) ##Calculated from Eq. (H_IRentedSoldMarket)
  H_INewOwnOccup[1]<<-H_IOwn[1]-H_IOwn[1]/(1+g_HIOwn[1])+H_IOwnOccupRented[1]+H_WOwnOccup[1]+H_IRentedVacant[1]+H_WOwnOccupVacant[1]#Number of new own-occupied houses by rentiers (Million houses) ##Calculated from Eq. (H_INewOwnOccup)
  H_INewOwnOccupG[1]<<-beta_H[1]*H_INewOwnOccup[1]#Number of new green own-occupied houses by rentiers (Million houses) ##Calculated from Eq. (H_INewOwnOccupG)
  H_INewOwnOccupC[1]<<-H_INewOwnOccup[1]-H_INewOwnOccupG[1]#Number of new conv. own-occupied houses by rentiers (Million houses) ##Calculated from Eq. (H_INewOwnOccupC)
  #Firms
  CO_HI[1]<<-Y[1]-CO_HW[1]-I[1]-CO_GOV[1]-I_Constr[1]-I_Refurb[1]#Consumption of investor households' (EUR trillion) ##Calculated from Eq. (Y)
 h_20<<-New_Constr[1]/(H_Constr[1]/(1+g_HConstr[1]))-h_21*(H_WNewOwnOccup[1]/(1+g_HWNewOwnOccup[1])+H_INewOwnOccup[1]/(1+g_HINewOwnOccup[1])+H_INewRented[1]/(1+g_HINewRented[1]))/(H_Constr[1]/(1+g_HConstr[1]))-h_22*g_PH[1]#Parameter in the housing investment function ##Calculated from Eq. (New_Constr)
  h_33<<-(p_H[1]-p_H[1]/(1+g_PH[1]))/(p_H[1]/(1+g_PH[1]))-h_3*(g_HD[1]-g_HS[1])#Parameter in the housing price equation ##Calculated from Eq. (p_H)
  TP_G[1]<<-Y[1]-W[1]-int_C*L_C[1]/(1+g_LC[1])-int_G*L_G[1]/(1+g_LG[1])#Total gross profit of firms (EUR trillion) ##Calculated from Eq. (TP_G)
  W[1]<<-s_W*Y[1]#Wage income (EUR trillion) ##Calculated from Eq. (W)
  TP[1]<<-TP_G[1]-TAX_F[1]-TAX_C[1]#Total profit of firms (EUR trillion) ##Calculated from Eq. (TP)
  s_F<<-(I[1]+I_Constr[1]-(g_L[1]/(1+g_L[1]))*L[1]-p_H[1]*(H_WNewOwnOccup[1]+H_INewOwnOccup[1]+H_INewRented[1]))/(TP[1]/(1+g_TP[1]))#Firms' retention rate ##Calculated from Eq. (L_C), (L_G), (L), (I) and (RP)
  RP[1]<<-s_F*TP[1]/(1+g_TP[1])#Retained profits (EUR trillion) ##Calculated from Eq. (RP)
  DP[1]<<-TP[1]-RP[1] #Distributed profits (EUR trillion)##Calculated from Eq. (DP)
  r[1]<<-TP[1]/K[1]#Rate of profit  ##Calculated from Eq. (r)
  alpha_01<<-alpha_1*u[1]+alpha_2*r[1]#Parameter in the investment function ##Calculated from Eq. (I)
  beta[1]<<-I_G[1]/I[1]#Share of green investment in total investment ##Calculated from Eq. (I_G)
  beta_0<<-beta[1]+beta_1*(int_G-int_C)#Parameter for the green investment share ##Calculated from Eq. (beta)
  I_C[1]<<-I[1]-I_G[1]#Conv. investment of firms (EUR trillion)##Calculated from Eq. (I_C)
  K_G[1]<<-((1+g_KG[1])/g_KG[1])*I_G[1]#Green capital of firms (EUR trillion) ##Calculated from Eq. (K_G)
  K_C[1]<<-((1+g_KC[1])/g_KC[1])*I_C[1]#Conv. capital of firms (EUR trillion) ##Calculated from Eq. (K_C)
  K[1]<<-K_G[1]+K_C[1]#Capital stock of firms (EUR trillion)##Calculated from Eq. (K)
  L_C[1]<<-L[1]-L_G[1] #Firms conv. loans (EUR trillion)##Calculated from Eq. (L)
  New_Constr[1]<<-H_Constr[1]-H_Constr[1]/(1+g_HConstr[1])#Number of new houses constructed (Million houses) ##Calculated from Eq. (H_Constr)
  H_ConstrG[1]<<-beta_H[1]*H_Constr[1]#Green new houses (Million houses) ##Calculated from Eq. (H_ConstrG)
  H_ConstrC[1]<<-H_Constr[1]-H_ConstrG[1]#Conv. new houses (Million houses) ##Calculated from Eq. (H_ConstrC)
  p_Constr<<-I_Constr[1]/H_Constr[1]#Price of constructed houses (EUR trillion per million houses) ##Calculated from Eq. (I_Constr)
  I_ConstrG[1]<<-beta_H[1]*I_Constr[1]#Investment in new green houses (EUR trillion) ##Calculated from Eq. (I_ConstrG)
  I_ConstrC[1]<<-I_Constr[1]-I_ConstrG[1]#Investment in new conv. houses (EUR trillion)##Calculated from Eq. (I_ConstrC)
  New_Refurb[1]<<-H_IRentedSoldG[1]/(1+g_HIRentedSoldG[1])+H_WOwnOccupG[1]/(1+g_HWOwnOccupG[1])+H_IOwnOccupRentedG[1]/(1+g_HIOwnOccupRentedG[1])+H_IRentedVacantG[1]/(1+g_HIRentedVacantG[1])+H_IRentedSoldVacantG[1]/(1+g_HIRentedSoldVacantG[1])+H_WOwnOccupVacantG[1]/(1+g_HWOwnOccupVacantG[1])#Number of refurbished houses (Million houses) ##Calculated from Eq. (New_Refurb)
  p_Refurb<<-I_Refurb[1]/H_Refurb[1]#Price of refurbished houses (EUR trillion per million houses) ##Calculated from Eq. (I_Refurb)
  H_ConstrVacant[1]<<-H_Constr[1]-H_WNewOwnOccup[1]-H_INewOwnOccup[1]-H_INewRented[1]#Vacant new houses (Million houses)##Calculated from Eq. (H_ConstrVacant)
  H_WOwnOccup[1]<<-H_WOwnOccupMarket[1]-H_WOwnOccupVacant[1]#Number of houses workers own occupy (Million houses) ##Calculated from Eq. (H_WOwnOccupVacant)
  H_WOwnOccupVacantG[1]<<-beta_H[1]*H_WOwnOccupVacant[1]#Number of green vacant houses own occupied houses (Million houses) ##Calculated from Eq. (H_WOwnOccupVacantG)
  H_WOwnOccupVacantC[1]<<-H_WOwnOccupVacant[1]-H_WOwnOccupVacantG[1]#Conv. vacant workers own occupied houses (Million houses) ##Calculated from Eq. (H_WOwnOccupVacantC)
  H_Vacant[1]<<-((1+g_HVacant[1])/g_HVacant[1])*(H_ConstrVacant[1]+H_IRentedSoldVacant[1]+H_IRentedVacant[1]+H_WOwnOccupVacant[1])#Total number of vacant houses (Million houses)##Calculated from Eq. (H_Vacant)
  H_VacantG[1]<<-beta_H[1]*H_Vacant[1]#Number of green vacant houses (Million houses)##Calculated from Eq. (H_VacantG)
  H_VacantC[1]<<-H_Vacant[1]-H_VacantG[1]#Number of conv. vacant houses (Million houses)##Calculated from Eq. (H_VacantC)
  H_Constr[1]<<-(g_HTotal[1]/(1+g_HTotal[1]))*H_Totalred[1]#Number of constructed houses (Million houses) ##Calculated from Eq. (H_Total)
  H_Total[1]<<-H_WOwn[1]+H_IOwn[1]+H_IRent[1]+H_Vacant[1]#Total number of houses (Million houses)##Calculated from Eq. (H_Totalred)
  H_Refurb[1]<<-((1+g_HRefurb[1])/g_HRefurb[1])*New_Refurb[1]#Number of refurbished houses (Million houses)##Calculated from Eq. (H_Refurb)
  H_TotalGred[1]<<-H_TotalG[1]#Total number of conventional houses, redundant (Million houses)##Calculated from Eq. (H_TotalG)
  H_TotalCred[1]<<-H_TotalC[1]#Total number of conventional houses, redundant (Million houses)##Calculated from Eq. (H_TotalC)
  H_TotalG[1]<<-H_WOwnG[1]+H_IOwnG[1]+H_IRentG[1]+H_VacantG[1]#Total number of green houses (Million houses)##Calculated from Eq. (H_TotalGred)
  H_TotalC[1]<<-H_WOwnC[1]+H_IOwnC[1]+H_IRentC[1]+H_VacantC[1]#Total number of conv. houses (Million houses)##Calculated from Eq. (H_TotalCred)
  H_Workers[1]<<-POP_W[1]/size#Number of houses worker live in (Million houses)##Calculated from Eq. (H_Workers)
  H_Rentiers[1]<<-POP_R[1]/size#Number of houses rentiers live in (Million houses)##Calculated from Eq. (H_Rentiers)
  POP_W[1]<<-prop_Workers*POP[1]#Population of workers (Million people) ##Calculated from Eq. (POP_W)
  POP_R[1]<<-POP[1]-POP_W[1]#Population of rentiers (Million people) ##Calculated from Eq. (POP_R)
  #Commercial banks
  BP[1]<<-int_C*L_C[1]/(1+g_LC[1])+int_G*L_G[1]/(1+g_LG[1])+int_LHC[1]*L_HC[1]/(1+g_LHC[1])+int_LHG[1]*L_NHG[1]/(1+g_LNHG[1])+int_S*SEC_B[1]/(1+g_SECB[1])+int_R*Repo[1]/(1+g_Repo[1])+FEE[1]+FVCP_D[1]-int_D*D[1]/(1+g_D[1])-int_A[1]*A[1]/(1+g_A[1])#Profit of the banks (EUR trillion) ##Calculated from Eq. (BP)
  D_HI[1]<<-D[1]-D_HW[1]#Deposits held by investor households (EUR trillion)##Calculated from Eq. (D)
  s_B<<-(CAP[1]*g_CAP[1]/(1+g_CAP[1])+DL_NH[1])/(BP[1]/(1+g_BP[1]))#Banks' retention rate ##Calculated from Eq. (CAP)
  BP_U[1]<<-s_B*BP[1]/(1+g_BP[1])#Undistributed profit of the banks (EUR trillion) ##Calculated from Eq. (BP_U)
  BP_D[1]<<-BP[1]-BP_U[1]#Distributed profit of the banks (EUR trillion)##Calculated from Eq. (BP_D)
  DL_NH[1]<<-def_HW[1]*(L_NHG[1]/(1+g_LNHG[1])+L_HC[1]/(1+g_LHC[1]))#Amount of defaulted loans com. banks (EUR trillion)##Calculated from Eq. (DL_NH)
  s_0<<-s[1]+s_1*(yield_M[1]-yield_MT)#Parameter linked to green securitised loans ##Calculated from Eq. (s)
  L_SHG[1]<<-s[1]*L_HG[1]#Securitised green housing loans (EUR trillion) ##Calculated from Eq. (L_SHG)
  L_NHG[1]<<-L_HG[1]-L_SHG[1]#Non-securitised green housing loans (EUR trillion)##Calculated from Eq. (L_NHG)
  h_1<<-HPM[1]/D[1]#Banks' reserve ratio  ##Calculated from Eq. (HPM)
  SEC_BN[1]<<-SEC_B[1]# ##Calculated from Eq. (SEC_BN)
  h_2<<-SEC_B[1]/D[1]#Banks' government securities-to-deposits ratio  ##Calculated from Eq. (SEC_B)
  A[1]<<-HPM[1]+L_G[1]+L_C[1]+L_NHG[1]+L_HC[1]+SEC_B[1]+Repo[1]-D[1]-CAP[1]#Advances (EUR trillion) ##Calculated from Eq. (A)
  A_N[1]<<-A[1]# ##Calculated from Eq. (A_N)
  CAP[1]<<-(HPM[1]+L_G[1]+L_C[1]+L_NHG[1]+L_HC[1]+SEC_B[1]+Repo[1])/lev_B[1]#Capital of banks (EUR trillion)##Calculated from Eq. (lev_B)
  CAR[1]<<-CAP[1]/(w_L*(L_G[1]+L_C[1]+L_NHG[1]+L_HC[1])+w_S*SEC_B[1]+w_H*HPM[1]+w_R*Repo[1]) #Capital adequacy ratio  ##Calculated from Eq. (CAR)
  r_1<<-r_2*dsr_HW[1]-r_3*(CAR[1]-CAR_min)#Parameter in the function of the credit rationing on housing loans##Calculated from Eq. (CR_H)
  CR_H[1]<<-CR_max/(1+r_0*exp(r_1-r_2*dsr_HW[1]+r_3*(CAR[1]-CAR_min)))#Degree of total credit rationing on housing loans ##Calculated from Eq. (CR_H)
  CR_HG[1]<<-(1+l_H3*(yield_M[1]-yield_MT))*CR_H[1]#Degree of green credit rationing on housing loans ##Calculated from Eq. (CR_HG)
  CR_HC[1]<<-(1-l_H3*(yield_M[1]-yield_MT))*CR_H[1]#Degree of conv. credit rationing on housing loans ##Calculated from Eq. (CR_HC)
  spr_HG[1]<<-int_LHG[1]-int_A[1]#Spread on green housing loans ##Calculated from Eq. (int_LHG)
  spr_HC[1]<<-int_LHC[1]-int_A[1]#Spread on conv. housing loans ##Calculated from Eq. (int_LHC)
  spr_H0<<-spr_H[1]+spr_H1*(CAR[1]-CAR_min)-spr_H2*dsr_HW[1]#Parameter in the spread on housing loans ##Calculated from Eq. (spr_H)
  spr_H[1]<<-spr_HG[1]/(1+spr_H3*(yield_M[1]-yield_MT)) #Spread on housing loans ##Calculated from Eq. (spr_HG)
  #Financial Vehicle Corporations (FVCs)
  s_FVC<<-(K_FVC[1]*g_Y[1]/(1+g_Y[1])+DL_FVC[1])/(FVCP[1]/(1+g_Y[1]))#FVCs retention rate ##Calculated from Eq. (K_FVC)
  s_IF<<-(K_IF[1]*g_Y[1]/(1+g_Y[1]))/(IFP[1]/(1+g_Y[1]))#IFs retention rate ##Calculated from Eq. (K_IF)
  epsilon_0<<-haircut[1]-epsilon_1*(yield_M[1]-yield_MT)#Parameter in the haircut##Calculated from Eq. (haircut)
  s_MMF<<-(K_MMF[1]*g_Y[1]/(1+g_Y[1]))/(MMFP[1]/(1+g_Y[1]))#MMFs retention rate##Calculated from Eq. (K_MMF)
  gamma_10<<-M_MMF[1]/(SH_MMF[1]/(1+g_Y[1]))-gamma_11*yield_M[1]-gamma_12*int_S#Parameter of MMFs portfolio choice ##Calculated from Eq. (M_MMF)
  gamma_20<<-SEC_MMF[1]/(SH_MMF[1]/(1+g_Y[1]))-gamma_21*yield_M[1]-gamma_22*int_S#Parameter of MMFs portfolio choice ##Calculated from Eq. (SEC_MMF)
  FVCP[1]<<-int_LHG[1]*L_SHG[1]/(1+g_Y[1])+int_S*SEC_FVC[1]/(1+g_Y[1])-FEE[1]-coupon_M[1]*m[1]/(1+g_m[1])#Profit of the FVCs (EUR trillion) ##Calculated from Eq. (ES)
  FVCP_U[1]<<-s_FVC*FVCP[1]/(1+g_Y[1])#Undistributed profit of the FVCs (EUR trillion)##Calculated from Eq. (FVCP_U)
  FVCP_D[1]<<-FVCP[1]-FVCP_U[1]#Distributed profit of the FVCs (EUR trillion)##Calculated from Eq. (FVCP_D)
  coupon_M[1]<<-yield_M[1]*p_Mbar#Green MBSs coupon payments ##Calculated from Eq. (coupon_M)
  FEE[1]<<-fee*L_SHG[1]/(1+g_Y[1])#Fee (EUR trillion) ##Calculated from Eq. (FEE)
  K_FVC[1]<<-SEC_FVC[1]+L_SHG[1]-p_Mbar*m[1]#Capital of FVCs (EUR trillion)##Calculated from Eq. (SEC_FVC)
  DL_FVC[1]<<-def_HW[1]*L_SHG[1]/(1+g_Y[1])#Amount of defaulted loans, FVCs (EUR trillion)##Calculated from Eq. (DL_FVC)
  m[1]<<-((1+g_m[1])/g_m[1])*((g_Y[1]/(1+g_Y[1]))*L_SHG[1]+DL_FVC[1])#Number of green MBSs issued (Million) ##Calculated from Eq. (m)
  M[1]<<-p_M[1]*m[1]#Value of the green MBSs (EUR trillion) ##Calculated from Eq. (p_M)
  #Investment Funds (IF)
  IFP[1]<<-coupon_M[1]*m_IF[1]/(1+g_m[1])+int_S*SEC_IF[1]/(1+g_Y[1])-int_R*Repo[1]/(1+g_Y[1])#Profit of the IFs (EUR trillion) ##Calculated from Eq. (IFP)
  IFP_U[1]<<-s_IF*IFP[1]/(1+g_Y[1])#Undistributed profit of the IFs (EUR trillion) ##Calculated from Eq. (IFP_U)
  IFP_D[1]<<-IFP[1]-IFP_U[1]#Distributed profit of the IFs (EUR trillion) ##Calculated from Eq. (IFP_D)
  haircut[1]<<-(K_IF[1]/(1+g_KIF[1]))/(M_IF[1]+SEC_IF[1])#Haircut on repos##Calculated from Eq. (M_IF)
  m_IF[1]<<-M_IF[1]/p_M[1]#Number of green MBSs owned by IFs (Million) ##Calculated from Eq. (m_IF)
  SEC_IF[1]<<-h_IF*SEC[1]#Government securities held by IFs (EUR trillion)##Calculated from Eq. (SEC_IF)
  Repo[1]<<-p_Mbar*m_IF[1]+SEC_IF[1]-K_IF[1]#Repo issued by IFs (EUR trillion)##Calculated from Eq. (Repo)
  K_IF[1]<<-(p_M[1]*m_IF[1]+SEC_IF[1])/lev_IF[1]#Capital of IFs (EUR trillion)##Calculated from Eq. (lev_IF)
  #Money Market Funds (MMF)
  MMFP[1]<<-coupon_M[1]*m_MMF[1]/(1+g_m[1])+int_S*SEC_MMF[1]/(1+g_Y[1])#Profit of the MMFs (EUR trillion) ##Calculated from Eq. (MMFP)
  MMFP_U[1]<<-s_MMF*MMFP[1]/(1+g_Y[1])#Undistributed profit of the MMFs (EUR trillion) ##Calculated from Eq. (MMFP_U)
  MMFP_D[1]<<-MMFP[1]-MMFP_U[1]#Distributed profit of the MMFs (EUR trillion) ##Calculated from Eq. (MMFP_D)
  M_MMF[1]<<-M[1]-M_IF[1]#Value of green MBSs held by MMFs (EUR trillion)##Calculated from Eq. (M)
  K_MMF[1]<<-p_Mbar*m_MMF[1]+SEC_MMF[1]-SH_MMF[1]#Capital of MMFs (EUR trillion)##Calculated from Eq. (SEC_MMF)
  m_MMF[1]<<-M_MMF[1]/p_M[1]#Number of gren MBSs held by MMFs (Million)##Calculated from Eq. (m_MMF)
  SH_MMF[1]<<-(p_M[1]*m_MMF[1]+SEC_MMF[1])/lev_MMF[1]#MMF shares (EUR trillion)##Calculated from Eq. (lev_MMF)
  r_M[1]<<-yield_M[1]+g_pM[1]#Rate of return on MBSs ##Calculated from Eq. (r_M)
  #Government
  tau_HI<<-TAX_HI[1]/(Y_HIG[1]/(1+g_Y[1]))# Investor households' tax rate ##Calculated from Eq. (TAX_HI)
  tau_F<<-(CO_GOV[1]-TAX_HW[1]-TAX_HI[1]-TAX_C[1]+int_S*SEC[1]/(1+g_SEC[1])-CBP[1]+int_SUB*L_HG[1]/(1+g_LHG[1])-(SEC[1]*g_SEC[1])/(1+g_SEC[1]))/(TP_G[1]/(1+g_TPG[1]))#Firms' tax rate ##Calculated from Eq. (SEC) and (GNS)
  GNS[1]<<-TAX[1]+CBP[1]-CO_GOV[1]-int_SUB*L_HG[1]/(1+g_Y[1])-int_S*SEC[1]/(1+g_Y[1])#Government net saving (EUR trillion) ##Calculated from Eq. (GNS)
  gov_C<<-CO_GOV[1]/(Y[1]/(1+g_Y[1])) #Share of government expenditure in output ##Calculated from Eq. (CO_GOV)
  TAX_HW[1]<<-tau_HW*Y_HWG[1]/(1+g_Y[1])#Taxes on worker households' disposable income (EUR trillion) ##Calculated from Eq. (TAX_HW)
  TAX_F[1]<<-tau_F*TP_G[1]/(1+g_Y[1]) #Taxes on firms' profits (EUR trillion) ##Calculated from Eq. (TAX_F)
  tau_C<<-TAX_C[1]/(EMIS_O[1]/(1+g_EMISO[1]))#Carbon tax (EUR trillion/GtCO2)##Calculated from Eq. (TAX_C)
  TAX[1]<<-TAX_HW[1]+TAX_HI[1]+TAX_F[1]+TAX_C[1] #Total taxes (EUR trillion) ##Calculated from Eq. (TAX) 
  #Central banks
  CBP[1]<<-int_A[1]*A[1]/(1+g_Y[1])+int_S*SEC_CB[1]/(1+g_Y[1])#Central bank profits (EUR trillion) ##Calculated from Eq. (CBP)
  SEC_HI[1]<<-SEC[1]-SEC_CB[1]-SEC_B[1]-SEC_FVC[1]-SEC_IF[1]-SEC_MMF[1]#Government securities held by investor households (EUR trillion) ##Calculated from Eq. (SEC_CB)
  SEC_CB[1]<<-HPM[1]+V_CB[1]-A[1]#Government securities held by central bank (EUR trillion) ##Calculated from Eq. (SEC_CBred)
  SEC_CBred[1]<<-SEC_CB[1] #Government securities held by central bank (EUR trillion)##Calculated from Eq. (SEC_CBred)
  int_A[1]<<-int_ref+(int_max-int_ref)*L_HC[1]/L_H[1]-(int_ref-int_min)*L_HG[1]/L_H[1]#Interest rate on advances ##Calculated from Eq. (int_A)
  V_CB[1]<<-0#Wealth of central bank (EUR trillion)##Calculated from Eq. (V_CB)
  #Emissions
  CI_H[1]<<-EMIS_H[1]/H_Total[1]#Carbon intensity of houses (GtCO2/Million)##Calculated from Eq. (EMIS_H)
  CI_O[1]<<-EMIS_O[1]/Y[1]#Carbon intensity of other emissions (GtCO2/EUR trillion) ##Calculated from Eq. (EMIS_O)
  #Auxiliary equations
  v<<-Y[1]/(K[1]*u[1])#Capital productivity  ##Calculated from Eq. (u) and (Y_pot)
  Y_pot[1]<<-v*K[1]#Potential output (EUR trillion)  ##Calculated from Eq. (Y_pot)
  lev[1]<<-L[1]/K[1] #Firms' leverage ratio ##Calculated from Eq. (lev)
  SEC_Y[1]<<-SEC[1]/Y[1]#Government debt-to-GDP ratio##Calculated from Eq. (SEC_Y)
  SEC_BY[1]<<-SEC_B[1]/Y[1]#Government securities held by banks-to-GDP ratio##Calculated from Eq. (SEC_BY)
  HPM_Y[1]<<-HPM[1]/Y[1] #High-powered money-to-GDP ratio ##Calculated from Eq. (HPM_Y)
  CBP_Y[1]<<-CBP[1]/Y[1]#Central bank profit–to–output ratio##Calculated from Eq. (CBP_Y)
  TAX_Y[1]<<-TAX[1]/Y[1] # ##Calculated from Eq. (TAX_Y)
  CAP_K[1]<<-CAP[1]/K[1]# ##Calculated from Eq. (CAP_K)
  V_CBK[1]<<-V_CB[1]/K[1]# ##Calculated from Eq. (V_CBK)
  HG_HC[1]<<-H_TotalG[1]/H_TotalC[1]# ##Calculated from Eq. (HG_HC)
  KG_KC[1]<<-K_G[1]/K_C[1]# ##Calculated from Eq. (KG_KC)
  g_Yper[1]<<-g_Y[1]*100# ##Calculated from Eq. (g_Yper)
  SEC_Yper[1]<<-SEC_Y[1]*100# ##Calculated from Eq. (SEC_Yper)
  WealthIndex[1]<<-(V_HI[1]/POP_R[1])/(V_HW[1]/POP_W[1])#Ratio of rentiers’ to workers’ wealth ##Calculated from Eq. (WealthIndex)
  IncomeIndex[1]<<-(Y_HI[1]/POP_R[1])/(Y_HW[1]/POP_W[1])#Ratio of rentiers’ to workers’ income ##Calculated from Eq. (IncomeIndex)
  PORT_SECHI[1]<<-SEC_HI[1]/(V_HI[1]/(1+g_VHI[1]))# ##Calculated from Eq. (PORT_SECHI)
  PORT_HDI[1]<<-(p_H[1]*H_IOwn[1])/(V_HI[1]/(1+g_VHI[1])) # ##Calculated from Eq. (PORT_HDI)
  PORT_SHMMF[1]<<-SH_MMF[1]/(V_HI[1]/(1+g_VHI[1])) # ##Calculated from Eq. (PORT_SHMMF)
  PORT_D[1]<<-D_HIN[1]/(V_HI[1]/(1+g_VHI[1])) # ##Calculated from Eq. (PORT_D)
  g_m[1]<<-(g_M[1]-g_pM[1])/(1+g_pM[1])#Growth rate of emissions##Calculated from Eq. (g_M) 
  g_HConstrGper[1]<<-g_HConstrG[1]*100#Growth rate of emissions##Calculated from Eq. (g_HConstrGper) 
  g_HWOwnGper[1]<<-g_HWOwnG[1]*100#Growth rate of emissions##Calculated from Eq. (g_HWOwnGper) 
  }
```

PARAMETERS FOR SCENARIOS

```{r}
Parameters_scenario2<-function(){
  int_SUB<<-0.0016
  s_0<<-(s[1]+s_1*(yield_M[1]-yield_MT))*1.5
  gamma_10<<-(M_MMF[1]/(SH_MMF[1]/(1+g_Y[1]))-gamma_11*yield_M[1]-gamma_12*int_S)*1.5
 }
Parameters_scenario3<-function(){
  int_SUB<<-0.02
  s_0<<-(s[1]+s_1*(yield_M[1]-yield_MT))*1.5
  gamma_10<<-(M_MMF[1]/(SH_MMF[1]/(1+g_Y[1]))-gamma_11*yield_M[1]-gamma_12*int_S)*1.5
}
####################
#BASELINE PARAMETERS
####################
Parameters_baseline<-function(){
  h_11<<-0.1#Parameter in the worker households' desired demand for houses (debt service ratio)  ##Selected from a reasonable range of values
  h_12<<-0.1#Parameter in the worker households' desired demand for houses (growth rate of housing prices)  ##Selected from a reasonable range of values
  h_21<<-0.01#Parameter in the firms' housing investment (housing demand)##Selected from a reasonable range of values
  h_22<<-0.01#Parameter in the firms' housing investment (growth rate of housing prices)##Selected from a reasonable range of values
  beta_H1<<-1#Parameter in the green share of houses (related to the sensitivity to the interest rates) ##Selected from a reasonable range of values
  r_3<<- 83.33333#-(r_3dCRdCARmax *((1+r_0)^2))/(CR_max*r_0)
  l_H3<<-2#Parameter in the green and conv. credit rationing on housing loans##Selected from a reasonable range of values
  spr_H1<<-0.03371429 #Parameter in the lending spread on housing loans (capital adequacy ratio) ##Selected from a reasonable range of values
  spr_H3<<-2#Parameter in the green and conv. lending spread on housing loans ##Selected from a reasonable range of values
  } 
#####################
#SENSITIVITY - Low responsiveness
#####################
Parameters_sensitivity1<-function(){
 h_11<<-0.1*0.5
 h_12<<-0.1*0.5
 h_21<<-0.1*0.5
 h_22<<-0.1*0.5
 beta_H1<<-0.5
 r_3<<- 83.33333*0.5
 l_H3<<-2*0.5
 spr_H1<<-0.03371429*0.5
 spr_H3<<-2*0.5
  }
######################
#SENSITIVITY - High responsiveness
######################
Parameters_sensitivity2<-function(){
 h_11<<-0.1*1.5
 h_12<<-0.1*1.5
 h_21<<-0.1*1.5
 h_22<<-0.1*1.5
 beta_H1<<-1.5
 r_3<<- 83.33333*1.5
 l_H3<<-2*1.5
 spr_H1<<-0.03371429*1.5
 spr_H3<<-2*1.5
 }

```

SYMBOLS AND VECTORS FOR ENDOGENOUS VARIABLES/PARAMETERS

```{r}
######################
#List of Greek letters
######################
greek_letters <- c("alpha", "theta", "epsilon", "omega", "sigma",
                   "delta", "gamma", "kappa", "lambda", "omicron",
                   "upsilon", "beta", "eta", "iota", "mu", "nu",
                   "xi", "pi", "rho", "phi", "chi", "psi", "zeta")
#############################################
#Symbols and vectors for endogenous variables
#############################################
code_body <- body(Equations) 
code_lines <- as.character(code_body)
Symbols_var <- regmatches(code_lines, regexpr("^[^[]+", code_lines)) 
Symbols_var <- sub("\\[t\\] <<-.*", "", Symbols_var)
Symbols_var <- Symbols_var[!Symbols_var %in% c("{", "}") & Symbols_var != ""]
for (v in 1:length(Symbols_var)){assign(noquote(paste(Symbols_var[v])), vector(length=n_periods))}
Symbols_var_sort <- sort(Symbols_var)
is_greek <- grepl(paste0("^(", paste(greek_letters, collapse="|"), ")"), Symbols_var_sort, ignore.case=TRUE)
Symbols_var_sort <- c(sort(Symbols_var_sort[!is_greek]), Symbols_var_sort[is_greek])
#######################
#Symbols for parameters
#######################
code_body <- body(Parameters_InitialValues) 
code_lines <- as.character(code_body) 
Symbols_par <- regmatches(code_lines, regexpr("^[^\\[]+<<-", code_lines)) 
Symbols_par <- sub("<<-$", "", Symbols_par) 
Symbols_par <- Symbols_par[Symbols_par != ""]  
Symbols_par_sort <- sort(Symbols_par) 
is_greek <- grepl(paste0("^(", paste(greek_letters, collapse="|"), ")"), Symbols_par_sort, ignore.case=TRUE)
Symbols_par_sort <- c(sort(Symbols_par_sort[!is_greek]), Symbols_par_sort[is_greek])
```

RUN THE MODEL AND THE SCENARIOS AND SAVE THE RESULTS

```{r}
for (j in 1:Scenarios){
  if (j<=3) {for (iterations in 1:20){Parameters_baseline() & Parameters_InitialValues()}}
  if (j>3 & j<=4) {for (iterations in 1:20){Parameters_sensitivity1() & Parameters_InitialValues()}}
  if (j>4 & j<=5) {for (iterations in 1:20){Parameters_sensitivity2() & Parameters_InitialValues()}}
  for (i in 2:n_periods){
    if (j==2 & i>=5){Parameters_scenario2()}
    if (j==3 & i>=5){Parameters_scenario3()}
    #Sensitivity High responsiveness
    if (j==4 & i>=5){Parameters_scenario3()}
    #Sensitivity Low responsiveness
    if (j==5 & i>=5){Parameters_scenario3()}
    
    for (iterations in 1:20){Equations(t=i)}
  }
  #######################################################################
  #Create tables with the variables in the same order as in the equations
  #######################################################################
  tablename<-paste("Variables",j, sep="")
  values<-setNames(data.frame(matrix(ncol = length(Symbols_var), nrow = n_periods)), Symbols_var)
  for (v in 1:length(Symbols_var)){values[,v]<-eval(parse(text=(paste(noquote(Symbols_var[v])))))}
  assign (tablename,round(values, 8))
  #######################################################
  #Create tables with the variables listed alphabetically
  #######################################################
  tablename<-paste("Variables_sorted",j, sep="")
  values<-setNames(data.frame(matrix(ncol = length(Symbols_var_sort), nrow = n_periods)), Symbols_var_sort)
  for (v in 1:length(Symbols_var_sort)){values[,v]<-eval(parse(text=(paste(noquote(Symbols_var_sort[v])))))}
  assign (tablename,round(values, 6))
  #########################################################
  #Create a table with the parameters listed alphabetically
  #########################################################
  tablename<-paste("Parameters_sorted",j, sep="")
  values<-setNames(data.frame(matrix(ncol = length(Symbols_par_sort), nrow = 1)), Symbols_par_sort)
  for (v in 1:length(Symbols_par_sort)){values[,v]<-eval(parse(text=(paste(noquote(Symbols_par_sort[v])))))}
  assign (tablename,round(values,4))
  rm(values)
  ###############################
  #Save the tables as excel files
  ###############################
  write.csv(get(paste0("Variables",j)), paste0("Variables",j,".csv"))
  write.csv(get(paste0("Variables_sorted",j)), paste0("Variables-sorted",j,".csv"))
  write.csv(get(paste0("Parameters_sorted",j)), paste0("Parameters-sorted",j,".csv"))
  }
```

CHART INFO

```{r}
library(ggplot2)
library(reshape2)
library(ggthemes) 
library(showtext)
library(sysfonts)
library(showtextdb)
showtext_auto()
Colour1="#000000" 
Colour2="#009E73" 
Colour3="#D55E00" 
Colour4="#0072B2"
Linetype1="solid"
Linetype2="solid" 
Linetype3="solid"
Linetype4="solid"
pch1=26
pch2=26
pch3=26
pch4=26
Size1=0.8
Size2=0.8
Size3=0.8
Size4=0.8
Scenario1="Baseline"
Scenario2="Green securitisation"
Scenario3="Green securitisation and green loan subsidy"
Scenario4="Green sec. and green loan subsidy - Case I"
Scenario5="Green sec. and green loan subsidy - Case II"
Periods<-1:n_periods   

Chart3<-function(fig_title, variable, label, min, max, sce1, sce2, sce3, legend_x, legend_y){
  eval(parse(text=(paste0("Line1=Variables", sce1, "[,c('",variable,"')]")))) 
  eval(parse(text=(paste0("Line2=Variables", sce2, "[,c('",variable,"')]")))) 
  eval(parse(text=(paste0("Line3=Variables", sce3, "[,c('",variable,"')]")))) 
  dataframe<<-data.frame(Periods, Line1, Line2, Line3)
  data_long<<-melt(dataframe, id ="Periods")
  
  plot<-ggplot(data=data_long, aes(x=Periods, y=value, colour=variable, linetype=variable, linewidth=variable, shape=variable)) + 
    geom_line(aes(linetype = variable, linewidth = variable)) + 
    geom_point(aes(shape = variable)) +  
    scale_color_manual(name=NULL, labels=c(eval(parse(text=(paste0("Scenario",sce1)))), eval(parse(text=(paste0("Scenario",sce2)))), eval(parse(text=(paste0("Scenario",sce3))))), values=c(Colour1, Colour2, Colour3))+
    scale_linetype_manual(name=NULL, labels=c(eval(parse(text=(paste0("Scenario",sce1)))), eval(parse(text=(paste0("Scenario",sce2)))), eval(parse(text=(paste0("Scenario",sce3))))), values=c(Linetype1, Linetype2, Linetype3)) +
    scale_linewidth_manual(name=NULL, labels=c(eval(parse(text=(paste0("Scenario",sce1)))), eval(parse(text=(paste0("Scenario",sce2)))), eval(parse(text=(paste0("Scenario",sce3))))), values=c(Size1, Size2, Size3))  +
    scale_shape_manual(name=NULL, labels=c(eval(parse(text=(paste0("Scenario",sce1)))), eval(parse(text=(paste0("Scenario",sce2)))), eval(parse(text=(paste0("Scenario",sce3))))), values=as.numeric(c(pch1,pch2,pch3)))+
    theme_bw()+
    theme(text=element_text(family="lato"),
          axis.title=element_text(size=32, colour="black"),
          axis.text=element_text(size=30, colour="black"),
          axis.ticks = element_line(colour = "black"),
          legend.position=c(legend_x, legend_y),
          legend.title=element_blank(),
          legend.text=element_text(size=30, colour="black"),
          legend.key.width = unit(1, "cm"),
          legend.key.height = unit(0, "cm"),
          legend.key=element_blank(),
          legend.background=element_blank(),
          legend.box.background=element_blank(), 
          plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"),
          panel.border=element_rect(color = "black", linewidth=0.8),
          panel.grid.major = element_line(linewidth = 0.1, linetype = 'solid', colour = "grey"),
          panel.grid.minor = element_line(linewidth = 0.1, linetype = 'solid', colour = "grey"))+
    labs(y =label, x ="Year")+
    geom_rect(aes(xmin = 1, xmax = n_periods, ymin=min, ymax=max),fill = "transparent")+
    coord_cartesian(ylim = c(min, max))+
        scale_x_continuous(expand = c(0, 0),
                       breaks = c(n_periods - 27, n_periods - 20, n_periods - 15, n_periods - 10, n_periods - 5, n_periods),
                       labels = c(2023, 2030, 2035, 2040, 2045, 2050)) +
    scale_y_continuous(expand = c(0, 0))
  ggsave(fig_title, plot, width = 6, height = 4, dpi = 300)
}

Chart4<-function(fig_title, variable, label, min, max, sce1, sce2, sce3, sce4, legend_x, legend_y){
  eval(parse(text=(paste0("Line1=Variables", sce1, "[,c('",variable,"')]")))) 
  eval(parse(text=(paste0("Line2=Variables", sce2, "[,c('",variable,"')]")))) 
  eval(parse(text=(paste0("Line3=Variables", sce3, "[,c('",variable,"')]")))) 
  eval(parse(text=(paste0("Line4=Variables", sce4, "[,c('",variable,"')]"))))  
  dataframe<<-data.frame(Periods, Line1, Line2, Line3, Line4)
  data_long <- melt(dataframe, id = "Periods")
  
  plot<-ggplot(data=data_long, aes(x=Periods, y=value, colour = variable, linetype=variable, linewidth=variable, shape=variable)) + 
    geom_line()+
    geom_point() +
    scale_color_manual(name=NULL, labels=c(eval(parse(text=(paste0("Scenario",sce1)))), eval(parse(text=(paste0("Scenario",sce2)))), eval(parse(text=(paste0("Scenario",sce3)))), eval(parse(text=(paste0("Scenario",sce4))))), 
                       values=c(Colour1, Colour2, Colour3, Colour4))+
    scale_linetype_manual(name=NULL, labels=c(eval(parse(text=(paste0("Scenario",sce1)))), eval(parse(text=(paste0("Scenario",sce2)))), eval(parse(text=(paste0("Scenario",sce3)))), eval(parse(text=(paste0("Scenario",sce4))))), 
                          values=c(Linetype1, Linetype2, Linetype3, Linetype4)) +
    scale_linewidth_manual(name=NULL, labels=c(eval(parse(text=(paste0("Scenario",sce1)))), eval(parse(text=(paste0("Scenario",sce2)))), eval(parse(text=(paste0("Scenario",sce3)))), eval(parse(text=(paste0("Scenario",sce4))))),
                      values=c(Size1, Size2, Size3, Size4))  +
    scale_shape_manual(name=NULL, labels=c(eval(parse(text=(paste0("Scenario",sce1)))), eval(parse(text=(paste0("Scenario",sce2)))), eval(parse(text=(paste0("Scenario",sce3)))), eval(parse(text=(paste0("Scenario",sce4))))), 
                       values=as.numeric(c(pch1,pch2,pch3, pch4)))+
    theme_bw()+
    theme(text=element_text(family="lato"),
          axis.title=element_text(size=31, colour="black"),
          axis.text=element_text(size=30, colour="black"),
          axis.ticks = element_line(colour = "black"),
          legend.position=c(legend_x, legend_y),
          legend.title=element_blank(),
          legend.text=element_text(size=30, colour="black"),
          legend.key.width = unit(1, "cm"),
          legend.key.height = unit(0, "cm"),
          legend.key=element_blank(),
          legend.background=element_blank(),
          legend.box.background=element_blank(), 
          plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"),
          panel.border=element_rect(color = "black", linewidth=0.8),
          panel.grid.major = element_line(linewidth = 0.1, linetype = 'solid', colour = "grey"),
          panel.grid.minor = element_line(linewidth = 0.1, linetype = 'solid', colour = "grey"))+
    labs(y =label, x ="Year")+
    geom_rect(aes(xmin = 1, xmax = n_periods, ymin=min, ymax=max),fill = "transparent")+
   scale_x_continuous(expand = c(0, 0),
                       breaks = c(n_periods - 27, n_periods - 20, n_periods - 15, n_periods - 10, n_periods - 5, n_periods),
                       labels = c(2023, 2030, 2035, 2040, 2045, 2050)) +
    scale_y_continuous(expand = c(0, 0))
  ggsave(fig_title, plot, width = 6, height = 4, dpi = 300)
}
```

CREATE CHARTS

```{r}
Chart3(fig_title="SB;Fig2-a-s.jpeg", variable='s',label="Share of securitised loans",min=0.05,max=0.2,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-b-CR_H.jpeg", variable='CR_H',label="Total credit rationing",min=0.1,max=0.3,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-c-CAR.jpeg", variable='CAR',label="Capital adequacy ratio",min=0.11,max=0.125,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-d-g_LH.jpeg", variable='g_LH',label="Growth rate of mortgages",min=0.01,max=0.03,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-e-g_Yper.jpeg", variable='g_Yper',label="Growth rate of output (%)",min=1.75,max=2.75,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-f-p_M.jpeg", variable='p_M',label="Price of MBSs",min=0.9,max=1.1,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-g-SEC_Yper.jpeg", variable='SEC_Yper',label="Government debt-to-GDP (%)",min=85,max=92,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-h-beta_H.jpeg", variable='beta_H',label="Share of green houses",min=0.32,max=0.38,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-i-g_pHper.jpeg", variable='g_PHper',label="Growth rate of housing prices (%)",min=-0.05,max=0.1,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-j-dsr_HW.jpeg", variable='dsr_HW',label="Household debt service ratio",min=0.17,max=0.19,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-k-lev_IF.jpeg", variable='lev_IF',label="Leverage ratio of IFs",min=5,max=7,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-l-lev_MMF.jpeg", variable='lev_MMF',label="Leverage ratio of MMFs",min=2,max=2.4,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-m-EMIS_O.jpeg", variable='EMIS_O',label=expression("Other CO" [2]*" emissions (Gt)"),min=0,max=4,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-n-EMIS_H.jpeg", variable='EMIS_H',label=expression("Housing CO" [2]*" emissions (Gt)"),min=0,max=2,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-o-CI_H.jpeg", variable='CI_H',label="Carbon int. housing emissions",min=0,max=0.05,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-p-CI_O.jpeg", variable='CI_O',label="Carbon int. other emissions",min=0,max=0.25,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-q-lev.jpeg", variable='lev',label="Firm leverage",min=0,max=0.2,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-r-lev_HW.jpeg", variable='lev_HW',label="Household leverage",min=0.8,max=1.1,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-s-lev_B.jpeg", variable='lev_B',label="Leverage ratio of banks",min=10,max=25,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-t-def_HW.jpeg", variable='def_HW',label="Default rate on loans",min=0.018,max=0.022,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-u-yield_M.jpeg", variable='yield_M',label="Yield for MBSs",min=0,max=0.1,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-v-g_LHG.jpeg", variable='g_LHG',label="Growth rate of green mortgages",min=0,max=0.3,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-w-g_LHC.jpeg", variable='g_LHC',label="Growth rate of conv. mortgages",min=-0.1,max=0.1,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-x-CR_HG.jpeg", variable='CR_HG',label="Green credit rationing",min=0.1,max=0.3,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-y-CR_HC.jpeg", variable='CR_HC',label="Conv. credit rationing",min=0.1,max=0.3,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z1-spr_H.jpeg", variable='spr_H',label="Total spread",min=0.0075,max=0.0125,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z2-spr_HG.jpeg", variable='spr_HG',label="Green spread",min=0.0075,max=0.0125,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z3-spr_HC.jpeg", variable='spr_HC',label="Conv. spread",min=0.0075,max=0.0125,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z4-illiqWH.jpeg", variable='illiq_HW',label="Illiqduidity ratio",min=0.95,max=1.05,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z5-g_HD.jpeg", variable='g_HD',label="Growth rate of housing demand",min=-0.8,max=0.8,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z6-g_HS.jpeg", variable='g_HS',label="Growth rate of housing supply",min=-0.3,max=0.3,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z7-rent.jpeg", variable='rent',label="Rent rate",min=0.015,max=0.22,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z8-g_HDrent.jpeg", variable='g_HDrent',label="Growth rate of demanded rented houses",min=-1,max=4,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z9-g_HSrent.jpeg", variable='g_HSrent',label="Growth rate of supplied rented houses",min=-0.3,max=0.3,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z10-r_SH.jpeg", variable='r_SH',label="Rate of return on shares issued by MMFs",min=0,max=0.05,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z11-yield_M.jpeg", variable='yield_M',label="Yield of MBSs",min=0,max=0.05,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z12-g_MMMF.jpeg", variable='g_MMMF',label="Growth rate of the value of green MBSs held by MMFs ",min=-0.05,max=0.05,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z13-g_MIF.jpeg", variable='g_MIF',label="Growth rate of the value of green MBSs held by IFs ",min=-0.08,max=0.05,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z14-g_mMMF.jpeg", variable='g_mMMF',label="Growth rate of the number of green MBSs held by MMFs ",min=-0.05,max=0.05,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z15-g_mIF.jpeg", variable='g_mIF',label="Growth rate of the number of green MBSs held by IFs ",min=-0.08,max=0.05,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)
Chart3(fig_title="SB;Fig2-z16-haircut.jpeg", variable='haircut',label="Haircut on repos",min=0.2,max=0.3,sce1=1, sce2=2, sce3=3, legend_x=0.35, legend_y=0.92)

#Figure A.1
Chart4(fig_title="SB;FigA.1-a-g_Yper.jpeg", variable='g_Yper',label="Growth rate of output (%)",min=1.75,max=2.75,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-b-g_PHper.jpeg", variable='g_PHper',label="Growth rate of housing prices (%)",min=-0.05,max=0.1,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-c-EMIS_H.jpeg", variable='EMIS_H',label=expression("Housing CO" [2]*" emissions (Gt)"),min=0,max=2,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-d-CAR.jpeg", variable='CAR',label="Capital adequacy ratio",min=0.11,max=0.125,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-e-dsr_HW.jpeg", variable='dsr_HW',label="Household debt service ratio",min=0.17,max=0.2,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-f-spr_HG.jpeg", variable='spr_HG',label="Green spread",min=0.0075,max=0.0125,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-g-spr_HC.jpeg", variable='spr_HC',label="Conv. spread",min=0.0075,max=0.0125,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-h-spr_H.jpeg", variable='spr_H',label="Total spread",min=0.0075,max=0.0125,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-i-beta_H.jpeg", variable='beta_H',label="Share of green houses",min=0.32,max=0.4, sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-j-g_HD.jpeg", variable='g_HD',label="Growth rate of housing demand",min=-0.03,max=0.2,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-k-CI_H.jpeg", variable='CI_H',label="Carbon int. housing emissions",min=0,max=0.01,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-l-g_HS.jpeg", variable='g_HS',label="Growth rate of housing supply",min=0,max=0.03,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-m-EMIS_O.jpeg", variable='EMIS_O',label=expression("Other CO" [2]*" emissions (Gt)"),min=0,max=4,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-n-p_H.jpeg", variable='p_H',label="Housing prices",min=0.21,max=0.23,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-o-p_M.jpeg", variable='p_M',label="Price of MBSs",min=0.5,max=1.5,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-p-lev_IF.jpeg", variable='lev_IF',label="Leverage ratio of IFs",min=4,max=10,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-q-lev_MMF.jpeg", variable='lev_MMF',label="Leverage ratio of MMFs",min=1,max=4,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-r-SEC_Yper.jpeg", variable='SEC_Yper',label="Government debt-to-GDP (%)",min=70,max=100,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-s-g_LH.jpeg", variable='g_LH',label="Growth rate of mortgages",min=0,max=0.05,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-t-CR_H.jpeg", variable='CR_H',label="Total credit rationing",min=0.1,max=0.3,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-u-CR_HG.jpeg", variable='CR_HG',label="Green credit rationing",min=0.1,max=0.3,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)
Chart4(fig_title="SB;FigA.1-v-CR_HC.jpeg", variable='CR_HC',label="Conv. credit rationing",min=0.1,max=0.3,sce1=1, sce2=3, sce3=4, sce4=5, legend_x=0.35, legend_y=0.92)

```

COUNT THE EQUATIONS

```{r}
code_lines<-capture.output(Equations) 
extract_variables<-function(code_lines) {
  valid_lines<-grep("<<-", code_lines, value = TRUE)
 matches<-regmatches(valid_lines, regexpr("^[^\\[]+", valid_lines))
  return(matches)
}
variables<-extract_variables(code_lines)
Equations_numbering<-cbind(Variable=variables, Equation = seq_along(variables))
Equations_numbering<- as.data.frame(Equations_numbering, stringsAsFactors = FALSE)
Equations_numbering$Variable <- trimws(Equations_numbering$Variable)
Equations_numbering$Equation <- trimws(Equations_numbering$Equation)
```

LATEX TABLE WITH INITIAL VALUES FOR ENDOGENOUS VARIABLES

```{r}
library(xtable)
########################################################
#Create a table with the symbols and the initial values
########################################################
column_names<-colnames(Variables_sorted1)
first_row_values<-round(Variables_sorted1[1, ],4)
transposed_first_row_values<-t(first_row_values)
Table_variables<-cbind(column_names,transposed_first_row_values)
colnames(Table_variables)<-c("Symbol","Initial value")
rownames(Table_variables) <- NULL
Table_variables <- as.data.frame(Table_variables)
############################
#Add the description column
############################
code_lines <- capture.output(Parameters_InitialValues) 
extract_comment <- function(var, code_lines) {
line_with_comment <- grep(paste0("\\b", var, "\\[1\\]<<-"), code_lines, value = TRUE)
  if (length(line_with_comment) > 0) {
    comment <- sub(".*#\\s*(.*?)\\s*##.*", "\\1", line_with_comment)
    return(trimws(comment))  
  } else {
    return(NA)  
  }
}
Table_variables$Description<- sapply(Table_variables$Symbol, extract_comment, code_lines= code_lines)
Table_variables<-Table_variables[, c("Symbol", "Description", "Initial value")]
############################
#Add the category column
############################
code_lines <- capture.output(Parameters_InitialValues) 
free_start <- grep("#Free", code_lines)
model_constrained_start <- grep("#Model-constrained", code_lines)
free_vars <- character(0)
model_constrained_vars <- character(0)
# Extract variables from 'Free' section
if (length(free_start) > 0) {
next_start <- min(c(model_constrained_start, length(code_lines) + 1))
  free_lines <- code_lines[(free_start + 1):(next_start - 1)]
  free_vars <- grep("<<-", free_lines, value = TRUE)
  free_vars <- sub("\\s*<<-.*", "", free_vars)  
  free_vars <- gsub("\\[.*", "", free_vars)  
  free_vars <- trimws(free_vars)  
}

# Extract variables from 'Model-constrained' section
if (length(model_constrained_start) > 0) {
 model_constrained_lines <- code_lines[(model_constrained_start + 1):length(code_lines)] 
  model_constrained_vars <- grep("<<-", model_constrained_lines, value = TRUE)
  model_constrained_vars <- sub("\\s*<<-.*", "", model_constrained_vars)  
  model_constrained_vars <- gsub("\\[.*", "", model_constrained_vars)  
  model_constrained_vars <- trimws(model_constrained_vars) 
}

# Function to categorise the variables
categorize_variables <- function(var) {
  if (var %in% free_vars) {
    return("Free")
  } else if (var %in% model_constrained_vars) {
    return("Model-constrained")
  } else {
    return(NA) 
  }
}

Table_variables$Category <- sapply(Table_variables$Symbol, categorize_variables)
Table_variables <- Table_variables[, c("Symbol", "Description", "Category", "Initial value")]
colnames(Table_variables)[colnames(Table_variables) == "Category"] <- "Variable category"

##############################
#Add the source/remarks column 
##############################
code_lines <- capture.output(Parameters_InitialValues) 
extract_comment <- function(var, code_lines) {
line_with_comment <- grep(paste0("\\b", var, "\\[1\\]<<-"), code_lines, value = TRUE)
  if (length(line_with_comment) > 0) {
      comment <- sub(".*##\\s*([^#]*?)\\s*$", "\\1", line_with_comment)
    return(trimws(comment))  
  } else {
    return(NA)  
  }
}
Table_variables$Sources<- sapply(Table_variables$Symbol, extract_comment, code_lines= code_lines)
Table_variables<-Table_variables[, c("Symbol", "Description", "Variable category", "Initial value","Sources")]
colnames(Table_variables)[colnames(Table_variables) == "Sources"] <- "Source/remarks"
##########################################################
#Add the number of equations in the source/remarks column
##########################################################
replace <- function(Table_variables, Equations_numbering) {
  lookup <- setNames(as.character(Equations_numbering[, 2]), Equations_numbering[, 1])
  variable_pattern <- paste0("\\b(", paste(names(lookup), collapse = "|"), ")\\b")
  Table_variables[, 5] <- sapply(Table_variables[, 5], function(x) {
    if (is.na(x)) {
      return("")  
    }
        x <- trimws(x)
    for (var in names(lookup)) {
      if (grepl(var, x)) {
        x <- gsub(paste0("\\b", var, "\\b"), lookup[var], x)
        }
    }
    return(x)
  })
  return(Table_variables)
}
  Table_variables<- replace(Table_variables, Equations_numbering)
##########################
#Create the table in latex
##########################
Table_variables$Symbol<- paste0("$", Table_variables$Symbol, "$")
Latex_table_variables<- xtable(Table_variables)
Latex_code <- capture.output(print(Latex_table_variables,  include.rownames = FALSE, sanitize.colnames.function = function(x) paste0("\\textbf{", x, "}"), type = "latex"))
Latex_code<-gsub("\\\\verb\\|([^|]+)\\|", "\\1", Latex_code)
Latex_code<-gsub("_(\\w+)", "_{\\1}", Latex_code, perl=TRUE)
Latex_code<-gsub("\\^(\\w+)", "^{\\1}", Latex_code, perl=TRUE)
Latex_code<-gsub("\\\\\\$", "\\$", Latex_code)
Latex_code<-gsub("\\\\_", "_", Latex_code)
Latex_code<-gsub("(\\w+_\\{\\w+\\})", "\\$\\1\\$", Latex_code)
Latex_code<-gsub("(\\w+\\^\\{[^}]+\\})", "\\$\\1\\$", Latex_code)
Latex_code<-gsub("\\$\\$", "\\$", Latex_code)

for (greek in greek_letters) {

  Latex_code <- gsub(
    paste0("\\$(.*?)", "(?<![a-zA-Z0-9])", greek, "(?![a-zA-Z0-9])", "(.*?)\\$"), 
    paste0("\\$", "\\\\", greek, "\\$", "\\1\\2"), 
    Latex_code, ignore.case = TRUE, perl = TRUE
  )
 Latex_code <- gsub(paste0("(", greek, ")(_)([a-zA-Z0-9]+)"), 
                     paste0("\\\\", greek, "_{\\3}"), Latex_code)
 Latex_code <- gsub(paste0("(", greek, ")(_\\{)([a-zA-Z0-9]+)(\\})"), 
                     paste0("\\\\", greek, "_{\\3}"), Latex_code)
 Latex_code <- gsub("\\\\b\\\\eta", "\\\\beta", Latex_code)
 Latex_code <- gsub("th\\\\eta", "\\theta", Latex_code)
 Latex_code <- gsub(paste0("(", greek, ")(?=\\s)"), 
                     paste0("\\\\", greek), Latex_code, perl = TRUE)
 Latex_code <- gsub(paste0("(", greek, ")(?=[A-Z])"), 
                     paste0("\\\\", greek, " "), Latex_code, perl = TRUE)
 Latex_code <- gsub(paste0("(", greek, ")(?=\\$)"), 
                     paste0("\\\\", greek), Latex_code, perl = TRUE)
 Latex_code <- gsub(paste0("\\\\", greek), 
                     paste0("\\", greek), Latex_code)
 
}
 
Latex_code<-gsub("\\\\begin\\{tabular\\}\\{lllll\\}", "\\\\begin{tabular}{lp{6cm}llp{5cm}}", Latex_code)
Latex_code <- gsub("\\\\begin\\{tabular\\}", "\\\\begin{longtable}", Latex_code)
Latex_code <- gsub("\\\\end\\{tabular\\}", "\\\\end{longtable}", Latex_code)
Latex_code <- gsub("\\\\begin\\{table\\}", "", Latex_code)       
Latex_code <- gsub("\\\\end\\{table\\}", "", Latex_code)  
Latex_code <- gsub("\\[ht\\]", "", Latex_code)
writeLines(Latex_code, "Latex_Table_variables.tex")
Latex_preamble <- "
\\documentclass{article}
\\usepackage[a4paper, left=1cm, right=1cm, top=2cm, bottom=2cm]{geometry} 
\\usepackage{longtable}
\\begin{document}
"
Latex_footer <- "
\\end{document}
"
Full_latex_code <- paste(Latex_preamble, paste(Latex_code, collapse = "\n"), Latex_footer, sep = "\n")
writeLines(Full_latex_code, "Latex_Table_variables.tex")
```

LATEX TABLE WITH PARAMETER VALUES

```{r}
library(xtable)
########################################################
#Create a table with the symbols and the parameter values
########################################################
column_names<-colnames(Parameters_sorted1)
first_row_values<-round(Parameters_sorted1[1, ],4)
transposed_first_row_values<-t(first_row_values)
Table_parameters<-cbind(column_names,transposed_first_row_values)
colnames(Table_parameters)<-c("Symbol","Value")
rownames(Table_parameters)<- NULL
Table_parameters<-as.data.frame(Table_parameters)
Table_parameters$Symbol<-trimws(Table_parameters$Symbol)
############################
#Add the description column
############################
code_lines<-capture.output(Parameters_InitialValues) 
extract_comment<-function(par, code_lines) {
line_with_comment <- grep(paste0("\\b", par,"\\s*<<-"), code_lines, value = TRUE)
  if (length(line_with_comment) > 0) {
    comment <- sub(".*#\\s*(.*?)\\s*##.*", "\\1", line_with_comment)
    return(trimws(comment))  
  } else {
    return(NA)  
  }
}
Table_parameters$Description<- sapply(Table_parameters$Symbol, extract_comment, code_lines= code_lines)
Table_parameters<-Table_parameters[, c("Symbol", "Description", "Value")]
########################
#Add the category column
########################
code_lines <- capture.output(Parameters_InitialValues) 
free_start <- grep("#Free", code_lines)
data_determined_start <- grep("#Data-determined", code_lines)
model_constrained_start <- grep("#Model-constrained", code_lines)
free_pars <- character(0)
model_constrained_pars <- character(0)

# Extract variables from 'Free' section
if (length(free_start) > 0) {
next_start <- min(c(model_constrained_start, length(code_lines) + 1))
  free_lines <- code_lines[(free_start + 1):(next_start - 1)]
  free_pars <- grep("<<-", free_lines, value = TRUE)
  free_pars <- sub("\\s*<<-.*", "", free_pars)  
  free_pars <- trimws(free_pars)  
}


# Extract variables from 'Model-constrained' section
if (length(model_constrained_start) > 0) {
  model_constrained_lines <- code_lines[(model_constrained_start + 1):length(code_lines)] 
  model_constrained_pars <- grep("<<-", model_constrained_lines, value = TRUE)
  model_constrained_pars <- sub("\\s*<<-.*", "", model_constrained_pars)  
  model_constrained_pars <- trimws(model_constrained_pars) 
}

# Function to categorize the parameters
categorize_parameters <- function(par) {
  if (par %in% free_pars) {
    return("Free")
  } else if (par %in% model_constrained_pars) {
    return("Model-constrained")
  } else {
    return(NA) 
  }
}

Table_parameters$Category<-sapply(Table_parameters$Symbol, categorize_parameters)
Table_parameters<-Table_parameters[, c("Symbol", "Description", "Category", "Value")]
colnames(Table_parameters)[colnames(Table_parameters) == "Category"] <- "Parameter category"
##############################
#Add the source/remarks column 
##############################
code_lines<-capture.output(Parameters_InitialValues) 
extract_comment<-function(par, code_lines) {
line_with_comment <- grep(paste0("\\b", par,"\\s*<<-"), code_lines, value = TRUE)
  if (length(line_with_comment) > 0) {
    comment <- sub(".*##\\s*([^#]*?)\\s*$", "\\1", line_with_comment)
    return(trimws(comment))  
  } else {
    return(NA)  
  }
}

Table_parameters$Sources<- sapply(Table_parameters$Symbol, extract_comment, code_lines= code_lines)
Table_parameters<-Table_parameters[, c("Symbol", "Description", "Parameter category", "Value","Sources")]
colnames(Table_parameters)[colnames(Table_parameters) == "Sources"] <- "Source/remarks"

##########################################################
#Add the number of equations in the source/remarks column
##########################################################
replace <- function(Table_parameters, Equations_numbering) {
  lookup <- setNames(as.character(Equations_numbering[, 2]), Equations_numbering[, 1])
  variable_pattern <- paste0("\\b(", paste(names(lookup), collapse = "|"), ")\\b")
  Table_parameters[, 5] <- sapply(Table_parameters[, 5], function(x) {
    if (is.na(x)) {
      return("")  
    }
        x <- trimws(x)
    for (var in names(lookup)) {
      if (grepl(var, x)) {
        x <- gsub(paste0("\\b", var, "\\b"), lookup[var], x)
        }
    }
    return(x)
  })
  return(Table_parameters)
}
  Table_parameters<- replace(Table_parameters, Equations_numbering)

####################################
#Create the table in Latex
####################################
Table_parameters$Symbol<- paste0("$", Table_parameters$Symbol, "$")
Latex_table_parameters<- xtable(Table_parameters)
Latex_code <- capture.output(print(Latex_table_parameters,  include.rownames = FALSE, sanitize.colnames.function = function(x) paste0("\\textbf{", x, "}"), type = "latex"))
Latex_code<-gsub("\\\\verb\\|([^|]+)\\|", "\\1", Latex_code)
Latex_code<-gsub("_(\\w+)", "_{\\1}", Latex_code, perl=TRUE)
Latex_code<-gsub("\\^(\\w+)", "^{\\1}", Latex_code, perl=TRUE)
Latex_code<-gsub("\\\\\\$", "\\$", Latex_code)
Latex_code<-gsub("\\\\_", "_", Latex_code)
Latex_code<-gsub("(\\w+_\\{\\w+\\})", "\\$\\1\\$", Latex_code)
Latex_code<-gsub("(\\w+\\^\\{[^}]+\\})", "\\$\\1\\$", Latex_code)
Latex_code<-gsub("\\$\\$", "\\$", Latex_code)

for (greek in greek_letters) {
 Latex_code <- gsub(paste0("\\$(.*?)\\$", "(?<![a-zA-Z0-9])", greek, "(?![a-zA-Z0-9])"), 
                     paste0("\\$", "\\\\", greek, "\\$", "\\1"), Latex_code, ignore.case = TRUE, perl = TRUE)
 Latex_code <- gsub(paste0("(", greek, ")(_)([a-zA-Z0-9]+)"), 
                     paste0("\\\\", greek, "_{\\3}"), Latex_code)
 Latex_code <- gsub(paste0("(", greek, ")(_\\{)([a-zA-Z0-9]+)(\\})"), 
                     paste0("\\\\", greek, "_{\\3}"), Latex_code)
 Latex_code <- gsub("\\\\b\\\\eta", "\\\\beta", Latex_code)
 Latex_code <- gsub("th\\\\eta", "\\theta", Latex_code)
 Latex_code <- gsub(paste0("(", greek, ")(?=\\s)"), 
                     paste0("\\\\", greek), Latex_code, perl = TRUE)
 Latex_code <- gsub(paste0("(", greek, ")(?=[A-Z])"), 
                     paste0("\\\\", greek, " "), Latex_code, perl = TRUE)
 Latex_code <- gsub(paste0("(", greek, ")(?=\\$)"), 
                     paste0("\\\\", greek), Latex_code, perl = TRUE)
}

Latex_code<-gsub("\\\\begin\\{tabular\\}\\{lllll\\}", "\\\\begin{tabular}{lp{6cm}llp{5cm}}", Latex_code)
Latex_code <- gsub("\\\\begin\\{tabular\\}", "\\\\begin{longtable}", Latex_code)
Latex_code <- gsub("\\\\end\\{tabular\\}", "\\\\end{longtable}", Latex_code)
Latex_code <- gsub("\\\\begin\\{table\\}", "", Latex_code)       
Latex_code <- gsub("\\\\end\\{table\\}", "", Latex_code)  
Latex_code <- gsub("\\[ht\\]", "", Latex_code)
writeLines(Latex_code, "Latex_Table_parameters.tex")
Latex_preamble <- "
\\documentclass{article}
\\usepackage[a4paper, left=1cm, right=1cm, top=2cm, bottom=2cm]{geometry} 
\\usepackage{longtable}
\\begin{document}
"
Latex_footer <- "
\\end{document}
"
Full_latex_code <- paste(Latex_preamble, paste(Latex_code, collapse = "\n"), Latex_footer, sep = "\n")
writeLines(Full_latex_code, "Latex_Table_parameters.tex")

```

EQUATIONS IN LATEX FORMAT

```{r}
Latex_code<-capture.output(Equations) 
Latex_code<-Latex_code[grep("<<-",Latex_code)]
Latex_code<-gsub("<<-", "=",Latex_code)
Latex_code<- gsub("_(\\w+\\[t(-1)?\\])", "_{\\1}", Latex_code)
Latex_code<- gsub("_(\\w+)", "_{\\1}", Latex_code)
Latex_code<- gsub("(\\w+)_\\{(\\w+)\\}(\\[t(-1)?\\])", "\\1_{\\2\\3}", Latex_code)
Latex_code<- gsub("(?<!\\{)\\[t\\](?!\\})", "_{[t]}", Latex_code, perl = TRUE)
Latex_code<- gsub("(?<!\\{)\\[t-1\\](?!\\})", "_{[t-1]}", Latex_code, perl = TRUE)
Latex_code<- gsub("exp\\(([^)]+)\\)", "e^{\\1}", Latex_code)
Latex_code<- gsub("([^=]+)=([^/]+)\\/([^\\s]+)", "\\1=\\frac{\\2}{\\3}", Latex_code)
Latex_code<- gsub("frac", "\\\\frac", Latex_code)
Latex_code<- gsub("\\\\frac\\{\\(([^)]+)\\)\\}\\{([^}]+)\\}", "\\\\frac{\\1}{\\2}", Latex_code)
Latex_code<-gsub("\\[t\\]", "t", Latex_code)
Latex_code<-gsub("\\[t-1\\]", "t-1", Latex_code)
Latex_code<-gsub("pmin", "min", Latex_code)
Latex_code<-gsub("pmax", "max", Latex_code)
Latex_code <- gsub("log\\((\\w+_\\{\\w+\\})\\)", "ln\\1", Latex_code)


for (greek in greek_letters) {
  
Latex_code <- gsub(paste0("(?<!\\\\)\\b(", greek, ")(?=\\b|_)"), 
                   paste0("\\\\", "\\1"), Latex_code, perl = TRUE)
Latex_code <- gsub(paste0("(\\\\", greek, ")(?=[a-zA-Z])"), 
                     "\\1 ", Latex_code, perl = TRUE)
Latex_code <- gsub(paste0("(\\\\", greek, ")(_)([a-zA-Z0-9]+)"), 
                     "\\1_{\\3}", Latex_code, perl = TRUE)
Latex_code <- gsub(paste0("(\\\\", greek, ")(_\\{)([a-zA-Z0-9]+)(\\})"), 
                    "\\1_{\\3}", Latex_code, perl = TRUE)
Latex_code <- gsub("\\\\b\\\\eta", "\\\\beta", Latex_code)
Latex_code <- gsub("th\\\\eta", "\\theta", Latex_code)
Latex_code <- gsub(paste0("(", greek, ")(?=\\s)"), 
                  paste0("\\\\", greek), Latex_code, perl = TRUE)
Latex_code <- gsub(paste0("(", greek, ")(?=[A-Z])"), 
                 paste0("\\\\", greek, " "), Latex_code, perl = TRUE)

}

Latex_code<-gsub("\\*", " ", Latex_code)
Latex_code<-gsub("\\\\cdot", "", Latex_code)

generate_latex_with_label <- function(Latex_code) {
  lhs <- strsplit(Latex_code, "=")[[1]][1]
  lhs <- gsub("[[:space:]]", "", lhs)  
  Latex_code<- paste0("\\begin{equation}\n", 
                      "\\label{eq:", lhs, "}\n",
                       Latex_code, "\n", 
                       "\\end{equation}")
  return(Latex_code)

}  


Final_latex_code <- sapply(Latex_code, generate_latex_with_label)

for (greek in greek_letters) {
  Final_latex_code <- gsub(
    paste0("eq:\\\\", greek), 
    paste0("eq:", greek), 
    Final_latex_code, 
    ignore.case = TRUE
  )

}
  
Latex_preamble <- "
\\documentclass{article}
\\usepackage{amsmath}
\\usepackage[a4paper, left=2cm, right=2cm, top=2cm, bottom=2cm]{geometry} 
\\begin{document}
"

Latex_footer <- "
\\end{document}
"
Latex_code <- paste(Latex_preamble, paste(Final_latex_code, collapse = "\n"), Latex_footer, sep = "\n")
writeLines(Latex_code, "Latex_Equations.tex")
```

BASELINE MODEL

```{r}
sce <- 1
if (sce == 1) {
var1<-sprintf ("%.3f", Variables1[2, "g_Y"])
var2<-sprintf ("%.3f", Variables1[3, "g_Y"])
var3<-sprintf ("%.3f", Variables1[27, "g_Y"])
var4<-sprintf ("%.3f", Variables1[12, "HG_HC"])
var5<-sprintf ("%.3f", Variables1[12, "KG_KC"])
var6<-sprintf ("%.3f", Variables1[1, "H_WOwn"])
var7<-sprintf ("%.3f", Variables1[1, "H_IRent"])
var8<-sprintf ("%.3f", Variables1[1, "H_IOwn"])
var9<-sprintf ("%.3f", Variables1[1, "H_Vacant"])
var10<-sprintf ("%.3f", Variables1[1, "H_Total"])
var11<-sprintf ("%.3f", Variables1[1, "H_Totalred"])
var12<-sprintf ("%.3f", Variables1[1, "H_WNewOwnOccup"])
var13<-sprintf ("%.3f", Variables1[1, "H_IRentedSold"])
var14<-sprintf ("%.3f", Variables1[1, "H_WOwnOccup"])
var15<-sprintf ("%.3f", Variables1[1, "H_INewRented"])
var16<-sprintf ("%.3f", Variables1[1, "H_IOwnOccupRented"])
var17<-sprintf ("%.3f", Variables1[1, "H_ConstrVacant"])
var18<-sprintf ("%.3f", Variables1[1, "H_IRentedVacant"])
var19<-sprintf ("%.3f", Variables1[1, "H_IRentedSoldVacant"])
var20<-sprintf ("%.3f", Variables1[1, "H_WOwnOccupVacant"])
var21<-sprintf ("%.3f", Variables1[1, "H_INewOwnOccup"])
var22<-sprintf ("%.3f", Variables1[1, "H_IRentedSoldMarket"])
var23<-sprintf ("%.3f", Variables1[1, "H_IOwnOccupRentedMarket"])
var24<-sprintf ("%.3f", Variables1[1, "H_WOwnOccupMarket"])

cat ("SCENARIO", sce, " ")
cat ("g_Y(2024):", var1," ")
cat ("g_Y(2025):", var2," ")
cat ("g_Y(2050):", var3," ")
cat ("HG_HC(2034):", var4," ")
cat ("KG_KC(2034):", var5," ")
cat ("H_WOwn(2023):", var6," ")
cat ("H_IRent(2023):", var7," ")
cat ("H_IOwn(2023):", var8," ")
cat ("H_Vacant(2023):", var9," ")
cat ("H_Total(2023):", var10," ")
cat ("H_Totalred(2023):", var11," ")
cat ("H_WNewOwnOccup(2023):", var12," ")
cat ("H_IRentedSold(2023):", var13," ")
cat ("H_WOwnOccup(2023):", var14," ")
cat ("H_INewRented(2023):", var15," ")
cat ("H_IOwnOccupRented(2023):", var16," ")
cat ("H_ConstrVacant(2023):", var17," ")
cat ("H_IRentedVacant(2023):", var18," ")
cat ("H_IRentedSoldVacant(2023):", var19," ")
cat ("H_WOwnOccupVacant(2023):", var20," ")
cat ("H_INewOwnOccup(2023):", var21," ")
cat ("H_IRentedSoldMarket(2023):", var22," ")
cat ("H_IOwnOccupRentedMarket(2023):", var23," ")
cat ("H_WOwnOccupMarket(2023):", var24," ")
}
```